---
title: "Project 2 / Report"
output:
  html_document:
    toc: true
    toc_float: true
    df_print: paged
    theme: cerulean
    highlight: zenburn
  html_notebook: default
editor_options: 
  chunk_output_type: inline
---
  
# A conference survey 
  
```{r Init_lib_theme, message=FALSE, warning=FALSE}

# Deactivate messages and warnings from running code, show code chunks

# Start with loading all the necessary libraries
library(readr)
library(janitor)
library(dplyr)
library(tidyr)
library(rmarkdown)
library(ggplot2)
library(dplyr)
library(purrr)
library(stringr)
library(knitr)
library(kableExtra)

# Load personal theme for ggplot2
myTheme <- function(base_size = 7.5,
                    base_family = "sans",
                    base_line_size = base_size / 22,
                    base_rect_size = base_size / 22){
  theme_minimal(base_size=base_size,
                base_family=base_family,
                base_line_size=base_line_size,
                base_rect_size=base_rect_size) %+replace%
  theme(
  line = element_line(
    size = base_line_size,
    linetype = 1,
    lineend = "round",
    color = "grey75"
    ),
  text = element_text(
    face = "plain",
    color = "grey25",
    family = "sans",
    size = base_size,
    hjust = 0,
    vjust = 0,
    angle = 0,
    lineheight = 1,
    margin= margin(),
    debug=FALSE
    ),
  plot.background = element_rect(
    fill = "grey98",
    color = "grey75",
    size = 1,
    linetype = 1
    ),
  panel.background = element_rect(fill="grey95",color="grey75"),
  axis.line = element_line(color="grey50", size=0.25),
  axis.ticks = element_line(color="grey50", size=0.25),
  axis.text = element_text(face="bold", size = 9),
  axis.title = element_text(face = "bold", size = 11, hjust = 0.5, vjust = 0),
  legend.text = element_text(face = "bold"),
  legend.title = element_text(face = "bold", size = 8),
  panel.grid.major.x = element_blank(),
  panel.grid.major.y = element_line(color="grey75"),
  panel.grid.minor = element_blank(),
  plot.margin=unit(c(12,12,12,12), "points"),
  plot.title = element_text(face = "bold", size = 12),
  plot.subtitle = element_text(
    face = "italic",
    size = 10,
    margin = margin(3,0,12,0,"pt")
    ),
  complete = TRUE
)
}

```
  
-------------------------------------------------------------------  
  
*Some data was collected from a survey of participants at a conference in *
*the Netherlands. The participants were asked the following questions:*  
  
*-What university do you come from?*  
*-What is your position?*  
*-How many employees are there in your research group?*  
*-How many Ph.D. students are there in your research group?*  
*-How many postdocs are there in your research group?*  
*-How many professors are there in your research group?*  
  
  
```{r Data_import_prep, message=FALSE, warning=FALSE}

### Chunk of code to prepare the data in different tables

# Import the data (orinigal CSV files previously copied in the project folder)
tbl_survey_raw <- read_csv("survey.csv")

# Clean the data of import (rename unnamed columns, clean names)
tbl_survey_clean <- tbl_survey_raw %>% 
  rename(participant_id =X1) %>% 
  clean_names()  

```

  
-------------------------------------------------------------------  

## Part 1 / Answer 3 questions  
  
In the first part of this report, I will try to answer these 3 questions :  
  
*1.*  How many survey participants were there?  
*2.*  What are the data types of each column?  
*3.*  What are the top 3 universities with the most survey participants?  
  
  
  
--------------------------------------------------------------------  
  
```{r Var_p1.1, message=FALSE, warning=FALSE}

# Value of the number of participants
participants_count <- tbl_survey_clean %>% 
  summarise(participants_count = n()) %>% 
  pull() 

```
  
### *1.* How many survey participants were there?  
  
There were **`r participants_count`** participants in this survey.  
  
  
  
--------------------------------------------------------------------  
  
```{r Var_p1.2, message=FALSE, warning=FALSE}

# Get the data type of each column
list_col_datatype <- tbl_survey_clean %>% 
  map_chr(class)
#  OLD
#     map_chr() return a character vector (expected result)
#     Same as workflow 'map() %>% unlist()' but shorter and more readable
#  map(class) %>% 
#  unlist()

# And the column associated to the datatype list
list_col_names <- tbl_survey_clean %>% 
  colnames

# And merge into a tibble
tbl_columns <- bind_cols(name=list_col_names,datatype=list_col_datatype)

```
 
### *2.* What are the data types of each column?  
  
Here is a table showing the name (after cleanup) and data type for each column :  
  
  
```{r Tbl_p1.2, message=FALSE, warning=FALSE}

tbl_columns %>% 
  mutate(datatype=cell_spec(datatype, "html", align = "justify")) %>% 
  rename("Name"=name,"Data type"=datatype) %>% 
  kable("html", escape = F) %>% 
  kable_styling(bootstrap_options = c("striped", "condensed", "responsive"),
                font_size = 12) %>% 
  column_spec(column = 1, width = "4cm") %>% 
  column_spec(column = 2, width = "1cm")

```
  
  

--------------------------------------------------------------------  

### *3.* What are the top 3 universities with the most survey participants?  
  
```{r Var_p1.3, message=FALSE, warning=FALSE}

# Top 3 universities by number of participants
tbl_top3_universities_by_participants <- tbl_survey_clean %>% 
  count(university, sort = TRUE, name = "count_part_by_university")
# OLD
#     Replace workflow 'group_by() %>% summarise(n()) %>% arrange(desc(n)))' 
#     by 'count()' with parameters
#  group_by(university) %>% 
#  summarise(count_part_by_university=n()) %>% 
#  arrange(desc(count_part_by_university))

```
  
Here is a table showing the top 3 universities regarding the number of survey
participants :    

```{r Tbl_p1.3, message=FALSE, warning=FALSE}

tbl_top3_universities_by_participants %>% 
  mutate(count_part_by_university=cell_spec(
    count_part_by_university, "html", align = "justify")
    ) %>%
  top_n(3, count_part_by_university) %>% 
  rename("University"=university,
         "Number of participants"=count_part_by_university) %>% 
  kable("html", escape = F) %>% 
  kable_styling(bootstrap_options = c("striped", "condensed", "responsive"),
                font_size = 12) %>% 
  column_spec(column = 1, width = "4cm") %>% 
  column_spec(column = 2, width = "1cm")

```
  
  
  
-------------------------------------------------------------------  
  
  
## Part 2 / Horizontal bar graph  
  
For the second part of this report, here is a horizonzal bar graph of the 
number of survey participants according to their different position.  
  
```{r Graph_p2, message=FALSE, warning=FALSE}

summary_for_hbar_graph <- tbl_survey_clean %>% 
  count(position, sort = TRUE, name = "count_per_position")
# OLD (same as Var_p1.3) 
#     Replace workflow 'group_by() %>% summarise(n()) %>% arrange(desc(n)))' 
#     by 'count()' with parameters
#  group_by(position) %>% 
#  summarize(count_per_position=n()) %>% 
#  ungroup() %>% 
#  arrange(count_per_position)

# Reorder the data according to count_per_position (set 'levels' in table)
summary_for_hbar_graph$position <- factor(
  summary_for_hbar_graph$position, 
  levels = summary_for_hbar_graph$position[order(
    summary_for_hbar_graph$count_per_position
    )])

summary_for_hbar_graph %>% 
  ggplot(mapping = aes(x = position, y = count_per_position)) +
  geom_bar(aes(fill = position), stat="identity", position = "stack") +
  scale_fill_manual(
    "Position",
    values = c("Postdoc"="firebrick1",
               "PhD Student"="firebrick3",
               "Assistant Professor"="springgreen2",
               "Associate Professor"="springgreen3",
               "Professor"="springgreen4",
               "Principal"="deepskyblue1",
               "Head of graduate studies"="deepskyblue3",
               "Head of department"="deepskyblue4"
               )
    ) +
  coord_flip() +
  labs(
    title = "Number of participants by position",
    subtitle = str_glue("Simple graph showing a distribution of participants ",
                        "by position  "),
    x = "Position",
    y = "Number of participants"
    ) +
  myTheme() +
  theme(
    axis.title.x = element_text(margin = margin(6,3,3,3,"pt")),
    axis.title.y = element_text(hjust = 0.9),
    axis.text.x = element_text(
      size = 9, face = "bold",
      hjust = 0.5,
      margin = margin(3,0,0,0,"pt")
      ),
    axis.text.y = element_text(
      size = 9, face = "bold",
      margin = margin(0,6,0,0,"pt")
      ),
    legend.position = "none",
    panel.grid.major.x = element_line(color="grey75"),
    panel.grid.major.y = element_blank(),
    panel.grid.minor = element_line(color="grey75")
  )

```
  
### Part 2 Findings  
  
The number of participants by position follows the tendency of the number of 
people in universities (there are more students than professors, and more 
professors than Deans).  
  
  
-------------------------------------------------------------------  
    
  
## Part 3 / Correct column 'Sizes' and plot a bar chart of the new distribution
    
For the third part of this report, we have to correct the column 'sizes'. A
mistake due to a misunderstanding made the bins' size slightly different than
desired. After correction with a bit of code, I will present a bar plot of the 
new distribution of sizes.  
  
```{r Graph_p3, message=FALSE, warning=FALSE}

# Recalculate column 'sizes'
tbl_survey_clean <- tbl_survey_clean %>% 
  mutate(sizes=case_when(
    number_of_employees<=10 ~ "Small (0 to 10)",
    number_of_employees<=20 ~ "Medium (11 to 20)",
    number_of_employees<=100 ~ "Large (21 to 100)",
    TRUE ~ "Extra large (over 100)"
  ))

summary_tbl_survey_clean <- tbl_survey_clean %>% 
    count(sizes, sort = TRUE, name = "count_per_size")
# OLD (same as Var_p1.3) 
#     Replace workflow 'group_by() %>% summarise(n()) %>% arrange(desc(n)))' 
#     by 'count()' with parameters
#  group_by(sizes) %>% 
#  summarize(count_per_size=n()) %>% 
#  ungroup() %>% 
#  arrange(count_per_size)

# Reorder the data according to count_per_size (set 'levels' in table)
summary_tbl_survey_clean$sizes <- factor(
  summary_tbl_survey_clean$sizes, 
  levels = summary_tbl_survey_clean$sizes[order(
    summary_tbl_survey_clean$sizes
    )])

summary_tbl_survey_clean %>% 
  ggplot(mapping = aes(x = sizes, y = count_per_size)) +
  geom_bar(aes(fill = sizes), stat="identity", position = "stack") +
  scale_fill_manual(
    "Sizes",
    values = c("Extra large (over 100)"="deepskyblue4",
               "Large (21 to 100)"="deepskyblue3",
               "Medium (11 to 20)"="deepskyblue2",
               "Small (0 to 10)"="deepskyblue"
               )
    ) +
  labs(
    title = "Universities by size",
    subtitle = "Showing the number of employees of each university",
    x = "Size",
    y = "Number of employees"
    ) +
  geom_text(mapping = aes(label = count_per_size),
    family = "sans",
    fontface = "bold",
    size = 5,
    color = "darkslategray1",
    nudge_y = -1.2
    ) +
  myTheme() +
  theme(
    axis.title.x = element_text(margin = margin(12,3,3,3,"pt")),
    axis.title.y = element_text(margin = margin(3,12,3,3,"pt")),
    axis.text.x = element_text(
      size = 9, face = "bold",
      margin = margin(3,6,0,0,"pt"),
      hjust = 0.5,
      ),
    axis.text.y = element_text(
      size = 9, face = "bold",
      margin = margin(0,6,0,0,"pt")
      ),
    legend.position = "none"
  )

```
  
### Part 3 Findings  
    
Large universities seem to be well represented.  
As for a deeper analysis, I didn't find clues for the reason of this 
disparity...  
Extra large universities are very probably fewer than small to middle sized 
universities.  
Some hypothesis that middle sized university are more represented than small 
ones could be that they have bigger financial means to send employees to 
conferences. But this is an assumption with absolutely nothing to back it up.  
  
-------------------------------------------------------------------  
    
  
## Part 4 / Stacked horizontal bar plot  
  
For the fourth and last part of this report, I will present a horizontal 
stacked bar plot showing the role percentage per group.  
 
```{r Graph_p4, message=FALSE, warning=FALSE}

summary_survey_by_group <-tbl_survey_clean %>%
  mutate(
    pc_phd=number_of_ph_d_students/number_of_employees,
    pc_postdocs=number_of_postdocs/number_of_employees,
    pc_professors=number_of_professors/number_of_employees
    ) %>% 
  select(participant_id,starts_with("pc_")) %>%  
  gather(
    pc_phd,
    pc_postdocs,
    pc_professors,
    key = "group",
    value = "percentage"
    )

summary_survey_by_group %>% 
  ggplot(mapping = aes(x=participant_id,y=percentage)) +
  geom_bar(
    aes(fill=group),
    stat="identity",
    position = position_stack(vjust = 0.5),
    width=0.75
  ) +
  scale_x_continuous(breaks=c(0:29))+
  scale_y_continuous(labels = scales::percent) +
  coord_flip() +
# With this 'scale_fill_manual', I set the colors and for aesthetic purposes
# I invert the labels (with values of course!)
  scale_fill_manual(
    "Employee type",
    limits = c("pc_professors","pc_postdocs","pc_phd"),
    values = c(
      "pc_professors"="steelblue3",
      "pc_postdocs"="chartreuse3",
      "pc_phd"="tomato1"
    ),
    labels = c(
      "Professors",
      "Postdocs",
      "PhD Students"
    )
  ) +
    labs(
    title = "Employees role percentages for each group",
    subtitle = str_glue("Different research groups have a very different ",
                        "distribution of roles  "),
    x = "Research Group ID",
    y = "Percentage"
  ) +
  myTheme() +
  theme(
    axis.title.x = element_text(margin = margin(3,3,0,3,"pt")),
    axis.title.y = element_text(margin = margin(3,12,3,3,"pt")),
    axis.text.x = element_text(
      size = 7, face = "bold",
      margin = margin(3,3,0,0,"pt"),
      hjust = 0.5,
    ),
    axis.text.y = element_text(
      size = 6, face = "bold.italic",
      margin = margin(3,6,3,0,"pt"),
      vjust = 0.5, hjust = 1
    ),
    legend.position = "bottom",
    legend.direction = "horizontal",
    legend.justification = 0.4,
    legend.text = element_text(hjust = 0.5, vjust = 0.5),
    legend.title = element_text(hjust = 0.5, vjust = 0.5),
    panel.grid.minor.y = element_blank(),
    panel.grid.major.y = element_blank()
  )

```
  
### Part 4 Findings 

The composition of the research groups is very heterogeneous.  
Some groups (11 and 12) don't include any PhD students!  
  
    
-------------------------------------------------------------------  
   
This is it for the 2nd report of this final project... See you soon for the 
third report.  
**Thank you for your attention!**
  
  
