---
title: "Project 6 / Report"
output:
  html_document:
    toc: true
    toc_float: true
    df_print: paged
    theme: cerulean
    highlight: zenburn
  html_notebook: default
editor_options: 
  chunk_output_type: inline
---
  
# A record of Olympics medals

```{r Init_lib_theme, message=FALSE, warning=FALSE}

# Deactivate messages and warnings from running code, show code chunks

# Start with loading all the necessary libraries
library(tidyverse)
library(readxl)
library(janitor)
library(knitr)
library(kableExtra)
library(scales)
library(ggrepel)

# Load personal theme for ggplot2
myTheme <- function(base_size = 7.5,
                    base_family = "sans",
                    base_line_size = base_size / 22,
                    base_rect_size = base_size / 22){
  theme_minimal(base_size=base_size,
                base_family=base_family,
                base_line_size=base_line_size,
                base_rect_size=base_rect_size) %+replace%
  theme(
  line = element_line(
    size = base_line_size,
    linetype = 1,
    lineend = "round",
    color = "grey75"
    ),
  text = element_text(
    face = "plain",
    color = "grey25",
    family = "sans",
    size = base_size,
    hjust = 0,
    vjust = 0,
    angle = 0,
    lineheight = 1,
    margin= margin(),
    debug=FALSE
    ),
  plot.background = element_rect(
    fill = "grey98",
    color = "grey75",
    size = 1,
    linetype = 1
    ),
  panel.background = element_rect(fill="grey95",color="grey75"),
  axis.line = element_line(color="grey50", size=0.25),
  axis.ticks = element_line(color="grey50", size=0.25),
  axis.text = element_text(face="bold", size = 9),
  axis.title = element_text(face = "bold", size = 11, hjust = 0.5, vjust = 0),
  legend.text = element_text(face = "bold"),
  legend.title = element_text(face = "bold", size = 8),
  panel.grid.major.x = element_line(color="grey75", size=0.5),
  panel.grid.major.y = element_line(color="grey75", size=0.5),
  panel.grid.minor = element_line(color="grey90", size=0.25),
  plot.margin=unit(c(12,12,12,12), "points"),
  plot.title = element_text(face = "bold", size = 12),
  plot.subtitle = element_text(
    face = "italic",
    size = 10,
    margin = margin(3,0,12,0,"pt")
    ),
  complete = TRUE
)
}

```
  
```{r Data_import_prep, message=FALSE, warning=FALSE}

# Import all raw data from excel file

athletes <- read_excel("olympics.xlsx", sheet = "athletes") %>% 
  clean_names()

country <- read_excel("olympics.xlsx", sheet = "country") %>% 
  clean_names()

games <- read_excel("olympics.xlsx", sheet = "games") %>% 
  clean_names()

medals <- read_excel("olympics.xlsx", sheet = "medals") %>% 
  clean_names()

```
  
-------------------------------------------------------------------  
  
*In this sixth project, we will explore a dataset that contains data about* 
*athletes at the Olympic Games.*  
  
*The titles in the different parts of this report are the questions asked, *
*the content of the parts being the answers.*
  
  
-------------------------------------------------------------------  

## Part 1 / Have some athletes competed for different countries over time? 
  
  
  
```{r Data_prep_p1, message=FALSE, warning=FALSE}

# Count the number of athlete_id that have more than one country
country_by_athlete_occurrences <- country %>% 
  select(athlete_id, noc) %>%
  distinct() %>% 
  group_by(athlete_id) %>% 
  mutate(occurrences = n()) %>% 
  filter(occurrences>1) %>% 
  ungroup()

# Join with the names of these athletes
athletes_for_multiple_countries <- country_by_athlete_occurrences %>% 
  left_join(athletes, by = c("athlete_id"="id"))

# How many athletes have competed for >1 country
count_athletes_for_multiple_countries <- athletes_for_multiple_countries %>% 
  select(name) %>% 
  distinct() %>% 
  count() %>% 
  pull()

# What is the maximum number of countries encountered
max_athletes_for_multiple_countries <- athletes_for_multiple_countries %>% 
  summarise(max_count = max(occurrences)) %>% 
  pull()
  
# How many athletes have competed for 'max_value' countries per athlete
count_max_athletes_for_multiple_countries <- athletes_for_multiple_countries %>% 
  filter(occurrences==max_athletes_for_multiple_countries) %>% 
  select(name) %>% 
  distinct() %>% 
  count() %>% 
  pull()

count_of_countries <- country %>% 
  select(noc) %>% 
  distinct() %>% 
  count() %>% 
  pull()

count_of_athletes <- athletes %>% 
  count() %>% 
  pull()

```
  
The answer is **yes**. Some athletes have competed for different countries over 
time.  
  
In a total of **`r count_of_countries`** countries and 
**`r count_of_athletes`** athletes listed in our dataset, there are 
**`r count_athletes_for_multiple_countries`** athletes that have competed for 
different countries.  

There even are **`r count_max_athletes_for_multiple_countries`** athletes that 
have successively competed for **`r max_athletes_for_multiple_countries`** 
different countries.  
  
  
  
-------------------------------------------------------------------  

## Part 2 / Who are the ten athletes that took part in most games?  
  
  
  
```{r Data_prep_p2, message=FALSE, warning=FALSE}

# Count the number of athlete_id in the list of medals
athletes_by_games_occurrences <- country %>% 
  select(athlete_id, games) %>% 
  distinct() %>% 
  group_by(athlete_id) %>% 
  mutate(occurrences = n()) %>% 
  arrange(desc(occurrences)) %>% 
  ungroup()

# Filter the top 10 (12) athletes and add name
athletes_top10_by_games <- athletes_by_games_occurrences %>% 
  select(athlete_id,occurrences) %>% 
  distinct() %>% 
  top_n(10, occurrences) %>% 
  mutate(occurrences=str_c(occurrences," Olympic games")) %>%
  left_join(athletes, by = c("athlete_id"="id"))

# Generate a table view of the result
athletes_top10_by_games %>%  
  select(occurrences, name, sex) %>% 
  rename(
    "Participated to"=occurrences,
    "Athlete's name"=name,
    "Gender"=sex
  ) %>%
  kable(format = "html",escape=F) %>% 
  kable_styling(
    bootstrap_options = c("striped", "condensed", "responsive", "bordered"),
    font_size = 11
  )  %>% 
  column_spec(column = 1, width = "20%", bold = F) %>% 
  column_spec(column = 2, width = "70%", bold = T) %>% 
  column_spec(column = 3, width = "10%", bold = F) %>% 
  collapse_rows(columns = 1, valign = "top")

```
  
As there are 9 athletes that equally participated to 8 games, this is in fact 
a top twelve...  
  
  
  
-------------------------------------------------------------------  

## Part 3 / What athlete(s) kept a Gold medal for the longest time?  
  
  
 
```{r Function_p3+4, message=FALSE, warning=FALSE}

# Create a personal function to calculate and group the sequences of successive 
# games by a given group

build_sequence_id <- function(my_tibble){
  group_seq <- vector("integer", nrow(my_tibble))

  for (i in 1:nrow(my_tibble)){

  if (my_tibble$year_diff_valid[i]==0) {
    group_seq[i] = 1
    x = 1
  } else if (my_tibble$year_diff_valid[i]==-4 & 
             my_tibble$group_id[i-1]==my_tibble$group_id[i]) {
      group_seq[i] = x
  } else {
    x = x+1
    group_seq[i] = x
  }  
  
  }
  result <- group_seq %>% 
    enframe() %>% 
    select(value) %>% 
    rename("group_id_seq"="value")
}


```

```{r Data_import_prep_p3, message=FALSE, warning=FALSE}

# Select gold medals and arrange data to group by athlete and by event
# Add a column "year"
# Add a column "year_diff" that represents the number of years from previous row
gold_medals_per_year_and_athlete <- medals %>% 
  filter(medal=="Gold") %>% 
  mutate(year=as.numeric(str_sub(games, start = 1, end = 4))) %>% 
  select(athlete_id, sport, event, medal, year) %>% 
  arrange(athlete_id, desc(year)) %>% 
  group_by(athlete_id, event) %>% 
  mutate(gold_by_event=n()) %>% 
  arrange(athlete_id, event, desc(year))%>% 
  arrange(desc(gold_by_event)) %>% 
  mutate(year_diff=if_else(
    athlete_id==lag(athlete_id) & event==lag(event), 
    year-lag(year), 
    0, missing = 0)
    )

# As a few intervals between games are not of 4 years (1920, 1948)
# --> create a "twist" to set all special intervals to 4 years.
gold_medals_per_year_and_athlete <- gold_medals_per_year_and_athlete %>% 
  mutate(year_diff_valid=case_when(
    year_diff==-2 ~ -4,
    year_diff==-8 & lag(year)==1920 ~ -4,
    year_diff==-12 & lag(year)==1948 ~ -4,    
    TRUE ~ year_diff
    )
  )

group_index_p3 <- gold_medals_per_year_and_athlete %>% 
  arrange(athlete_id, sport, event, desc(year)) %>% 
  group_by(athlete_id, sport, event) %>% 
  group_indices(athlete_id, sport, event, year) %>% 
  enframe() %>% 
  ungroup() %>% 
  select(value) %>% 
  rename("group_id"="value")

gold_medals_per_year_and_athlete <- gold_medals_per_year_and_athlete %>% 
  arrange(athlete_id, sport, event, desc(year)) %>% 
  bind_cols(group_index_p3) 

gold_medals_per_year_and_athlete_seq <- gold_medals_per_year_and_athlete %>% 
  build_sequence_id()
  
gold_medals_per_year_and_athlete <- gold_medals_per_year_and_athlete %>% 
  bind_cols(gold_medals_per_year_and_athlete_seq) %>% 
  group_by(group_id, group_id_seq) %>% 
  mutate(count_successive_games=n()) %>% 
  ungroup()

# Generate a list of the top athletes with most successive gold medals for a
# given event
result_athletes_succ_gold <- gold_medals_per_year_and_athlete %>% 
  select(athlete_id, sport, event, count_successive_games, year) %>% 
  group_by(athlete_id, event) %>% 
  mutate(max_of_successive_games=max(count_successive_games)) %>% 
  ungroup() %>% 
  select(-count_successive_games) %>% 
  distinct() %>% 
  arrange(desc(max_of_successive_games)) %>% 
  filter(max_of_successive_games==max(max_of_successive_games)) %>% 
  mutate(min_year=min(year)) %>% 
  mutate(max_year=max(year)) %>% 
  left_join(athletes, by = c("athlete_id"="id")) %>% 
  select(
    sport, event, max_of_successive_games, 
    min_year, max_year, name, sex) %>% 
  mutate(sex=if_else(sex=="M", "man", "woman")) %>% 
  distinct()

```
  
The longest time that an athlete kept a Gold medal for a given event is during 
**`r max(pull(result_athletes_succ_gold, max_of_successive_games))`** successive 
games. There is only 
**`r nrow(distinct(result_athletes_succ_gold, athlete_id))`** athlete holding 
this record. It is a **`r pull(result_athletes_succ_gold, sex)`** 
and is named **`r pull(result_athletes_succ_gold, name)`**.  
**`r pull(result_athletes_succ_gold, name)`** started the successful sequence in 
**`r pull(result_athletes_succ_gold, min_year)`** and this ended in 
**`r pull(result_athletes_succ_gold, max_year)`**.  
This was in the **`r pull(result_athletes_succ_gold, sport)`** discipline, 
specifically in the **`r pull(result_athletes_succ_gold, event)`** event.  
  
  
  
-------------------------------------------------------------------  

## Part 4 / What country(ies) kept a Gold medal for the longest time?  
  
  
  
```{r Data_import_prep_p4, message=FALSE, warning=FALSE}

# Select gold medals and arrange data to group by country and by event
# Add a column "year"
# Add a column "year_diff" that represents the number of years from previous row
gold_medals_per_year_and_country <- medals %>% 
  filter(medal=="Gold") %>% 
  mutate(year=as.numeric(str_sub(games, start = 1, end = 4))) %>% 
  select(games, team, sport, event, medal, year) %>% 
  arrange(team, sport, event, desc(year)) %>% 
  distinct() %>% 
  group_by(team, sport, event) %>% 
  mutate(count_games_by_event=n()) %>% 
  arrange(team, sport, event, desc(year)) %>%
  mutate(group_row_index=row_number(team)) %>% 
  ungroup() %>% 
  mutate(year_diff=if_else(
    team==lag(team) & event==lag(event), 
    year-lag(year), 
    0, missing = 0)
    )

# As a few intervals between games are not of 4 years (1920, 1948)
# --> create a "twist" to set all special intervals to 4 years.
gold_medals_per_year_and_country <- gold_medals_per_year_and_country %>% 
  mutate(year_diff_valid=case_when(
    year_diff==-2 ~ -4,
    year_diff==-8 & lag(year)==1920 ~ -4,
    year_diff==-12 & lag(year)==1948 ~ -4,    
    TRUE ~ year_diff
    )
  ) %>% 
# As there are some games with only 2 years interval, change to 4 years for 
# simplicity while checking interval
  mutate(year_diff=if_else(year_diff==-2,-4,year_diff))

group_index_p4 <- gold_medals_per_year_and_country %>% 
  arrange(team, sport, event, desc(year)) %>% 
  group_by(team, sport, event) %>% 
  group_indices(team, sport, event, year) %>% 
  enframe() %>% 
  ungroup() %>% 
  select(value) %>% 
  rename("group_id"="value")

gold_medals_per_year_and_country <- gold_medals_per_year_and_country %>% 
  arrange(team, sport, event, desc(year)) %>% 
  bind_cols(group_index_p4) 

gold_medals_per_year_and_country_seq <- gold_medals_per_year_and_country %>% 
  build_sequence_id()
  
gold_medals_per_year_and_country <- gold_medals_per_year_and_country %>% 
  bind_cols(gold_medals_per_year_and_country_seq) %>% 
  group_by(group_id, group_id_seq) %>% 
  mutate(count_successive_games=n()) %>% 
  ungroup()

# Generate a list of the top teams with most successive gold medals for a
# given event
result_teams_succ_gold <- gold_medals_per_year_and_country %>% 
  group_by(group_id, group_id_seq) %>% 
  mutate(min_year=min(year), max_year=max(year)) %>% 
  ungroup %>% 
  select(team, sport, event, count_successive_games, min_year, max_year) %>% 
  group_by(team, event) %>% 
  mutate(max_of_successive_games=max(count_successive_games)) %>% 
  ungroup() %>% 
  filter(
    max_of_successive_games==max(max_of_successive_games),
    count_successive_games==max_of_successive_games
    ) %>% 
  select(-count_successive_games) %>% 
  distinct() %>% 
  arrange(desc(max_of_successive_games)) 

```
  
The longest time that a country kept a Gold medal for a given event is during 
**`r max(pull(result_teams_succ_gold, max_of_successive_games))`** successive 
games. There is only 
**`r nrow(distinct(result_teams_succ_gold, team))`** country holding 
this record: **`r pull(result_teams_succ_gold, team)`**.  
**`r pull(result_teams_succ_gold, team)`** started the successful sequence in 
**`r pull(result_teams_succ_gold, min_year)`** and this ended in 
**`r pull(result_teams_succ_gold, max_year)`**.  
This was in the **`r pull(result_teams_succ_gold, sport)`** discipline, 
specifically in the **`r pull(result_teams_succ_gold, event)`** event.    
  
  
  
-------------------------------------------------------------------  

## Part 5 / Who are the ten athletes that competed in the most events?  
  
  
  
```{r Data_prep_p5, message=FALSE, warning=FALSE}

athletes_by_events <- medals %>% 
  select(athlete_id, sport, event) %>% 
  distinct() %>% 
  group_by(athlete_id) %>% 
  mutate(occurrences=n()) %>% 
  ungroup()

athletes_top10_by_events <- athletes_by_events %>% 
  select(athlete_id, occurrences) %>%
  distinct() %>% 
  arrange(desc(occurrences)) %>% 
  top_n(10, occurrences) %>% 
  left_join(athletes, by = c("athlete_id"="id"))

```
  
  
Here is a table presenting the top **`r nrow(athletes_top10_by_events)`** 
athletes that have participated to the most events :  
  
```{r Data_view_prep_p5, message=FALSE, warning=FALSE}

# Generate a table view of the result
athletes_top10_by_events %>%
  select(occurrences, name, sex) %>% 
  mutate(occurrences=str_c(occurrences, " events")) %>% 
  rename(
    "Number of different events"=occurrences,
    "Name of athlete"=name,
    "Gender"=sex
  ) %>%
  kable(format = "html",escape=F) %>% 
  kable_styling(
    bootstrap_options = c("striped", "condensed", "responsive", "bordered"),
    font_size = 11
  )  %>% 
  column_spec(column = 1, width = "25%", bold = F) %>% 
  column_spec(column = 2, width = "60%", bold = T) %>% 
  column_spec(column = 3, width = "15%", bold = F)%>% 
  collapse_rows(columns = 1, valign = "top")

```
  
  
  
-------------------------------------------------------------------  

## Part 6 / Table showing the number of medals per country and per year  
  
  
  
```{r Data_prep_p6, message=FALSE, warning=FALSE}

# Get as variable the minimum count of medals to be in the top 15 countries 
filter_var_top15_countries <- medals %>% 
  filter(medal!="NA_character_") %>% 
  arrange(team) %>% 
  group_by(team) %>% 
  mutate(occurrences=n()) %>% 
  ungroup() %>% 
  select(team, occurrences) %>% 
  distinct() %>% 
  arrange(desc(occurrences)) %>% 
  top_n(15, occurrences) %>% 
  summarise(min(occurrences)) %>% 
  pull()
  
# Create table with the top 15 countries including number of medals per year  
medals_by_country_all_medals <- medals %>% 
  filter(medal!="NA_character_") %>% 
  arrange(team) %>% 
  group_by(team) %>% 
  mutate(occurrences=n()) %>% 
  ungroup() %>% 
  filter(occurrences>=filter_var_top15_countries) %>% 
  mutate(year=as.numeric(str_sub(games, start = 1, end = 4))) %>% 
  select(team, year) %>% 
  arrange(team, desc(year)) %>% 
  group_by(team, year) %>% 
  mutate(count_all_medals=n()) %>% 
  ungroup() %>% 
  group_by(team) %>% 
  mutate(total=n()) %>% 
  ungroup() %>% 
  distinct()

# Spread the table to have the desired result (rows=countries, columns=years)
tbl_medals_by_country_all_medals <- medals_by_country_all_medals %>% 
  spread(year, count_all_medals, fill = 0) %>% 
  arrange(desc(total)) %>% 
  select(-total)

```
  
Here is a table presenting the top 15 countries with their total number of 
medals per year (ordered by descending total of medals) :  
  
```{r Data_view_prep_p6, message=FALSE, warning=FALSE}

# Generate table for view in browser
tbl_medals_by_country_all_medals %>% 
  rename("Country"=team) %>%
  kable(format = "html",escape=F) %>% 
  kable_styling(
    bootstrap_options = c("striped", "condensed", "responsive", "bordered"),
    font_size = 11
  )  %>% 
  column_spec(column = 1, bold = T) %>% 
  scroll_box(width = "100%") 

```
  
  
  
-------------------------------------------------------------------  

## Part 7 / `r str_glue("Scatterplot showing the average height and weight of ",
                                          "competitors per sport")`  
  
  
  
```{r Data_prep_p7, message=FALSE, warning=FALSE}

# Eliminate athletes with no weight or height and calculate BMI
bmi_athletes <- athletes %>% 
  filter(height!="", weight!="") %>% 
  mutate(bmi=weight/((height/100)^2))

# Get all athletes for each sport (athletes participating in different sports
# are counted once for each sport)
sports_metadata <- bmi_athletes %>% 
  left_join(medals, by = c("id"="athlete_id")) %>% 
  select(id, sport, height, weight, bmi) %>% 
  distinct() 

# Summarise all data and get mean values for height, weight and bmi
summary_sports_metadata <- sports_metadata %>% 
  group_by(sport) %>% 
  summarise_at(.funs = mean, .vars = c("height", "weight", "bmi")) %>% 
  ungroup()

# Summary for additional informations
summary_sports_metadata_infos_1 <- summary_sports_metadata %>% 
  filter(height==max(height)) %>% 
  mutate(category="Max avg height") %>% 
  mutate(group="Max")
summary_sports_metadata_infos_2 <- summary_sports_metadata %>% 
  filter(height==min(height)) %>% 
  mutate(category="Min avg height") %>% 
  mutate(group="Min")
summary_sports_metadata_infos_3 <- summary_sports_metadata %>% 
  filter(weight==max(weight)) %>%
  mutate(category="Max avg weight")  %>% 
  mutate(group="Max")
summary_sports_metadata_infos_4 <- summary_sports_metadata %>% 
  filter(weight==min(weight)) %>% 
  mutate(category="Min avg weight") %>% 
  mutate(group="Min")
summary_sports_metadata_infos_5 <- summary_sports_metadata %>% 
  filter(bmi==max(bmi)) %>%
  mutate(category="Max avg BMI")  %>% 
  mutate(group="Max")
summary_sports_metadata_infos_6 <- summary_sports_metadata %>% 
  filter(bmi==min(bmi)) %>% 
  mutate(category="Min avg BMI") %>% 
  mutate(group="Min")
  
summary_sports_metadata_infos <- bind_rows(
  summary_sports_metadata_infos_1,
  summary_sports_metadata_infos_2,
  summary_sports_metadata_infos_3,
  summary_sports_metadata_infos_6,
  summary_sports_metadata_infos_5,
  summary_sports_metadata_infos_4
)
  

```


```{r Plot_prep_p7, message=FALSE, warning=FALSE}

# Generate scatterplot 
summary_sports_metadata %>% 
  ggplot(aes(x = height, y = weight)) +
  geom_point(
    size = 2, 
    shape = 21, 
    fill = "deepskyblue3", 
    color = "deepskyblue3", 
    alpha = 0.6
  ) +
  labs(
    title = "Average height vs Average weight",
    subtitle = str_glue("Visualisation of the average height and weight per ",
      "sport, including informations for min and max values"),
    x = "Height (in cm)",
    y = "Weight (in kg)",
    caption = str_glue(
      "There are ", 
      nrow(summary_sports_metadata), 
      " sports represented in this plot. \nBased on the measurements of ", 
      number(nrow(sports_metadata), big.mark = "'"),
      " athletes."
    )
  ) +
  xlim(160, 195) +
  ylim(35, 105) +
  # Add layer for additional informations
  geom_point(
    data = summary_sports_metadata_infos,
    mapping = aes(
      x = height, 
      y = weight,
      color = group
    ),
    shape = 1,
    size = 6,
    stroke = 2,
    show.legend = FALSE
  ) +
  geom_label_repel(
    summary_sports_metadata_infos,
    mapping = aes(
      x = height, 
      y = weight, 
      fill = group,
      label = str_c(sport, "\n", category)
    ),
    fontface = "bold",
    size = 3,
    show.legend = FALSE,
    position = position_nudge(x = 0, y = c(8, -8)),
    direction = "x",
    point.padding = 0,
    segment.alpha = 0
  )  +
  scale_color_manual(
    values = c("dodgerblue2","orangered2")
  )  +
  scale_fill_manual(
    values = c("deepskyblue","lightsalmon")
  ) +
  myTheme() +
  theme(
    axis.title.x = element_text(margin = margin(6,3,3,3,"pt")),
    axis.title.y = element_text(margin = margin(3,6,3,3,"pt")),
    axis.text.x = element_text(
      size = 9, face = "bold",
      margin = margin(3,6,0,0,"pt"),
      hjust = 0.5,
    ),
    axis.text.y = element_text(
      size = 9, face = "bold",
      margin = margin(0,3,0,0,"pt")
    ),
    plot.caption = element_text(face = "italic", size = 7)
  )

```
  
  
  
-------------------------------------------------------------------  

## Part 8 / Lineplot showing the number of medals given per year  
  
  
  
```{r Data_prep_p8, message=FALSE, warning=FALSE}

# Select and prepare the data
medals_per_year <- medals %>% 
  filter(medal!="") %>% 
  select(games, medal) %>% 
  mutate(year=as.numeric(str_sub(games, start = 1, end = 4))) %>%
  mutate(games=str_sub(games, start = 6, end = str_length(games))) %>% 
  arrange(desc(year), medal, games)

summary_medals_per_year <- medals_per_year %>% 
  group_by(games, year, medal) %>% 
  summarise(count=n()) %>% 
  ungroup()

# Get some values for caption in plot
min_year <- summary_medals_per_year %>% 
  select(year) %>% 
  distinct() %>% 
  filter(year==min(year)) %>% 
  pull()

max_year <- summary_medals_per_year %>% 
  select(year) %>% 
  distinct() %>% 
  filter(year==max(year)) %>% 
  pull()

```


```{r Plot_prep_p8, message=FALSE, warning=FALSE}

summary_medals_per_year$medal <- fct_relevel(
  summary_medals_per_year$medal, 
  levels = c("Gold", "Silver", "Bronze")
)

# Generate scatterplot 
summary_medals_per_year %>% 
  ggplot(aes(x = year, y = count, group = medal)) +
  geom_line(aes(color = medal),
    size = 1.5,
    alpha = 0.7
  )  +
  facet_wrap(vars(games), ncol = 1, scales = "free_y") +
  labs(
    title = "Medals per year and season",
    subtitle = str_glue("Visualisation of the number of medals by type and",
        " year, for Summer and Winter Games"),
    x = "Year",
    y = "Count of medals",
    color = "Medal",
    caption = str_glue(
      "Data available from year ", min_year, " to year ", max_year,
      "\nThe scales on the y-axis (Count of medals) have been adapted ",
      "for readability."
    )
  ) +
  scale_color_manual(
    values = c(
      "Gold"="gold",
      "Silver"="azure3",
      "Bronze"="darkgoldenrod3"
    )
  ) +
  myTheme() +
  theme(
    axis.title.x = element_text(margin = margin(6,3,3,3,"pt")),
    axis.title.y = element_text(margin = margin(3,6,3,3,"pt")),
    axis.text.x = element_text(
      size = 9, face = "bold",
      margin = margin(3,6,0,0,"pt"),
      hjust = 0.5,
    ),
    axis.text.y = element_text(
      size = 9, face = "bold",
      margin = margin(0,3,0,0,"pt")
    ),
    plot.caption = element_text(face = "italic", size = 7),
    strip.text = element_text(
      face = "bold.italic", 
      size = 9, 
      hjust = 0, 
      vjust = 0.5, 
      color = "grey25"
    )
  )

```
  
Since the 1980's, the global number of medals has dramatically increased.  
We can see through this plot that the average number of medals in Summer Games 
is just above 3 times the average of Winter Games in the recent years. In the 
1950's, there were 5 times less medals given during Winter Games than during 
Summer Games.  
The number of Gold, Silver and Bronze medals given is roughly the same for every 
Games.

  

