---
title: "Project 5 / Report"
output:
  html_document:
    toc: true
    toc_float: true
    df_print: paged
    theme: cerulean
    highlight: zenburn
  html_notebook: default
editor_options: 
  chunk_output_type: inline
---
  
# The Movie DB

```{r Init_lib, message=FALSE, warning=FALSE}

# Deactivate messages and warnings from running code, show code chunks

# Start with loading all the necessary libraries
library(dplyr)
library(tidyr)
library(rmarkdown)
library(purrr)
library(stringr)
library(knitr)
library(kableExtra)
library(httr)
library(magrittr)
# dplyr::rownames_to_column() deprecated, replaced by tibble::rownames_to_column
library(tibble) 

```

  
-------------------------------------------------------------------  
  
*In this fifth project, we will explore the data from The Movie DB, using *
*the API provided from the web.*  
  

  
-------------------------------------------------------------------  

## Part 1 / Create new requests from given examples 
  
For the first part of this report, the challenge is to send a few queries 
through the API of The Movie DB. Based on provided examples in the website, 
I will adapt these in order to answer 3 questions.  
  
Here are some informations from The Movie Database used in this exercise:  

- Genres :
  + Drama = ID 18
  + Family = ID 10751

- Actors :
  + Will Ferrell = ID 23659
  + Liam Neeson = ID 3896
  + Tom Cruise = ID 500
  
    
### 1. What are the highest grossing dramas from 2010?  
  
```{r Data_import_prep_p1.1, message=FALSE, warning=FALSE}

# Import the data from the internet site
# with_genres 18 = Drama
# sort by revenue.desc
# Extract the 'original_title', 'title' and 'release_date
qry_highest_grossing_dramas_2010 <- GET(
  str_glue("https://api.themoviedb.org/3/",
  "discover/movie?api_key=cae3b93dd5e2d16994763563ea0a2eb5",
  "&with_genres=18&primary_release_year=2010",
  "&sort_by=revenue.desc")) %>% 
  content() %>% 
  purrr::pluck("results") %>% 
  map(extract, c("original_title", "title", "release_date")) 

# Reshape data into a clean tibble 
result_highest_grossing_dramas_2010 <- qry_highest_grossing_dramas_2010 %>%
  enframe() %>% 
  unnest_wider(value) %>% 
  rename("#"=name)


# OLD
# Flatten the result to extract the data
#qry_highest_grossing_dramas_2010 <- qry_highest_grossing_dramas_2010 %>% 
#  content() %>% 
#  flatten()

# Extract the original_title as a 1 column tibble
#qry_list_original_title1 <- qry_highest_grossing_dramas_2010 %>% 
#  map(extract, "original_title") %>% 
#  flatten() %>% 
#  tibble() %>%
#  rename("original_title"=".") %>% 
#  filter(original_title!="NA")

# Extract the title as a 1 column tibble
#qry_list_title1 <- qry_highest_grossing_dramas_2010 %>% 
#  map(extract, "title") %>% 
#  flatten() %>% 
#  tibble()  %>%
#  rename("title"=".") %>% 
#  filter(title!="NA")

# Extract the release_date as a 1 column tibble
#qry_list_release_date1 <- qry_highest_grossing_dramas_2010 %>% 
#  map(extract, "release_date") %>% 
#  flatten() %>% 
#  tibble() %>% 
#  rename("release_date"=".") %>% 
#  filter(release_date!="NA")

# Binding the 3 tibbles to have one clean tibble for our answers
#result_highest_grossing_dramas_2010 <- bind_cols(
#  qry_list_original_title1,
#  qry_list_title1,
#  qry_list_release_date1
#  ) %>% 
#  rownames_to_column() %>% 
#  rename("#"="rowname")

```
  
Here is a table with the 10 highest grossing dramas from 2010:  

```{r Data_result_p1.1, message=FALSE, warning=FALSE}
result_highest_grossing_dramas_2010 %>%  
  head(10) %>% 
  rename(
    "Original title"=original_title,
    "Title"=title,
    "Release date"=release_date
  ) %>%
  kable(format = "html",escape=F) %>% 
  kable_styling(
    bootstrap_options = c("striped", "condensed", "responsive", "bordered"),
    font_size = 11
  )  
```  
  
  
### 2. Have Will Ferrell and Liam Neeson even been in a movie together?  
  
```{r Data_import_prep_p1.2, message=FALSE, warning=FALSE}

# Import the data from the internet site
# with_people 23659 = Will Ferrell and 3896 = Liam Neeson
# sort by popularity.desc
# Extract the 'original_title', 'title' and 'release_date
qry_Will_Ferrell_and_Liam_Neeson  <- GET(
  str_glue("https://api.themoviedb.org/3/",
  "discover/movie?api_key=cae3b93dd5e2d16994763563ea0a2eb5",
  "&with_people=23659,3896",
  "&sort_by=popularity.desc")) %>% 
  content() %>% 
  purrr::pluck("results") %>% 
  map(extract, c("original_title", "title", "release_date")) 

# Reshape data into a clean tibble 
result_Will_Ferrell_and_Liam_Neeson <- qry_Will_Ferrell_and_Liam_Neeson %>% 
  enframe() %>% 
  unnest_wider(value) %>% 
  rename("#"=name)


# OLD
# Flatten the result to extract the data
#qry_02_Will_Ferrell_and_Liam_Neeson <- qry_02_Will_Ferrell_and_Liam_Neeson %>% 
#  content() %>% 
#  flatten()

# Extract the original_title as a 1 column tibble
#qry_list_original_title2 <- qry_02_Will_Ferrell_and_Liam_Neeson %>% 
#  map(extract, "original_title") %>% 
#  flatten() %>% 
#  tibble() %>%
#  rename("original_title"=".") %>% 
#  filter(original_title!="NA")

# Extract the title as a 1 column tibble
#qry_list_title2 <- qry_02_Will_Ferrell_and_Liam_Neeson %>% 
#  map(extract, "title") %>% 
#  flatten() %>% 
#  tibble()  %>% 
#  rename("title"=".") %>% 
#  filter(title!="NA")

# Extract the release_date as a 1 column tibble
#qry_list_release_date2 <- qry_02_Will_Ferrell_and_Liam_Neeson %>% 
#  map(extract, "release_date") %>% 
#  flatten() %>% 
#  tibble() %>% 
#  rename("release_date"=".") %>% 
#  filter(release_date!="NA")

# Binding the 3 tibbles to have one clean tibble for our answers
#result_02_Will_Ferrell_and_Liam_Neeson <- bind_cols(
#  qry_list_original_title2,
#  qry_list_title2,
#  qry_list_release_date2
#  ) 

```
  
Here is a table with all the movies starring Will Ferrell and Liam Neeson:  

```{r Data_result_p1.2, message=FALSE, warning=FALSE}

result_Will_Ferrell_and_Liam_Neeson %>%  
  rename(
    "Original title"=original_title,
    "Title"=title,
    "Release date"=release_date
  ) %>%
  kable(format = "html",escape=F) %>% 
  kable_styling(
    bootstrap_options = c("striped", "condensed", "responsive", "bordered"),
    font_size = 11
  )  
```
  
    
### 3. Can you find kids movies with Tom Cruise in it?  
  

```{r Data_import_p1.3, message=FALSE, warning=FALSE}

# Import the data from the internet site
# with_people 500 = Tom Cruise 
# with_genres 10751 = Family
qry_Tom_Cruise_for_kids  <- GET(
  str_glue("https://api.themoviedb.org/3/",
  "discover/movie?api_key=cae3b93dd5e2d16994763563ea0a2eb5",
  "&with_people=500&with_genres=10751",
  "&sort_by=popularity.desc")) 

# result of query gives us only a header and no records...

```
  
Tom Cruise has never starred in a kids movie. 
  
  
  
-------------------------------------------------------------------  

## Part 2 / Create a query to find the ID of "Pixar" animation company  
  
For the second part of this report, I will create a query to search for 
**Pixar** in The Movie Database. From that result, I will extract the ID of 
the company.  
  
  
In [the API documentation from The Movie Database](https://developers.themoviedb.org/3/search/search-companies), 
the generated request looks like :  
  
*search/company?api_key=\<\<<api_key\>\>&query=Pixar&page=1*  
  
So let's send this request and save the result in a variable:  

```{r Data_import_p2.1, message=FALSE, warning=FALSE}

# Query to search all companies and retrieve informations in relation with
# "Pixar"
qry_Pixar_company  <- GET(
  str_glue("https://api.themoviedb.org/3/",
  "search/company?api_key=cae3b93dd5e2d16994763563ea0a2eb5",
  "&query=Pixar")) 

```
  
In order to retrieve the ID of **Pixar** animation company, I flatten the 
content of the result and build a tibble with the different values in columns.  
  
```{r Data_import_prep_p2.2, message=FALSE, warning=FALSE}

# Reshape the data to have a clean tibble
result_Pixar_company <- qry_Pixar_company %>% 
  content() %>% 
  purrr::pluck("results") %>% 
  map(extract, c("id", "name")) %>% 
  enframe() %>% 
  rename(index = name, value_list = value) %>% 
  unnest_wider(value_list) %>% 
  rename(company_name = name)


# OLD
# Extract the company name as a 1 column tibble
#qry_Pixar_company1 <- qry_Pixar_company %>% 
#  map(extract, "name") %>% 
#  flatten() %>% 
#  tibble() %>% 
#  rename("company_name"=".") %>% 
#  filter(company_name!="NA")

# Extract the ID as a 1 column tibble
#qry_Pixar_company2 <- qry_Pixar_company %>% 
#  map(extract, "id") %>% 
#  flatten() %>% 
#  tibble()  %>% 
#  rename("id"=".") %>% 
#  filter(id!="NA")

# Binding the 2 tibbles to have one clean tibble for our answers
#result_Pixar_company <- bind_cols(
#  qry_Pixar_company1,
#  qry_Pixar_company2
#  ) 

```
  
And then, I extract the ID from my tibble (filtered on **Pixar**).
  
```{r Data_extract_p2.3, message=FALSE, warning=FALSE}

# Retrieve ID of Pixar animation company
result_Pixar_ID <- result_Pixar_company %>% 
  filter(company_name=="Pixar") %>% 
  pull(id) %>% 
  first() %>% 
  as.numeric()

```
  
And I get a numeric value of **`r result_Pixar_ID`**, the ID of **Pixar** 
animation company.  
  
  
  
-------------------------------------------------------------------  

## Part 3 / Create a query to list all the movies from **Pixar**  
  
For the third part of this report, I will create a query to list all the 
movies from **Pixar**.  With this result, I will then convert it to a tibble 
showing the interesting informations.  
  
Here are the queries to retrieve all movies from **Pixar**. As there is a limit 
of 20 results per page and there are 23 movies in all, I had to create 2 
requests...  
As the extraction and conversion of the data is done twice, I create a personal 
function in order to keep the code (quite) short.   
  
```{r Data_import_prep_p3, message=FALSE, warning=FALSE}

# Queries to search all companies and retrieve informations in relation with
# "Pixar" // 2 queries necessary because of the limit of 20 results per page
qry_Pixar_movies1  <- GET(
  str_glue("https://api.themoviedb.org/3/",
  "discover/movie?api_key=cae3b93dd5e2d16994763563ea0a2eb5",
  "&include_adult=false&include_video=false&with_runtime.gte=60",
  "&sort_by=revenue.desc&page=1&with_companies=",result_Pixar_ID))

qry_Pixar_movies2 <- GET(
  str_glue("https://api.themoviedb.org/3/",
  "discover/movie?api_key=cae3b93dd5e2d16994763563ea0a2eb5",
  "&include_adult=false&include_video=false&with_runtime.gte=60",
  "&sort_by=revenue.desc&page=2&with_companies=",result_Pixar_ID))

# Personal function to get all the details and generate a tibble as result 
get_movie_details <- function(raw_data) {
  
  qry_movies <- raw_data %>% 
    content() %>%
    purrr::pluck("results") %>% 
    map(
      extract, c(
      "original_title", 
      "release_date", 
      "vote_average", 
      "overview"
      )
    ) %>% 
    enframe() %>% 
    unnest_wider(value) %>% 
    select(-name)
    
  
# OLD  
  # Extract the original title as a 1 column tibble
#  prep_movies1 <- qry_movies %>% 
#  map(extract, "original_title") %>% 
#  flatten() %>% 
#  tibble() %>% 
#  rename("original_title"=".") 

  # Extract the release_date as a 1 column tibble
#  prep_movies2 <- qry_movies %>% 
#  map(extract, "release_date") %>% 
#  flatten() %>% 
#  tibble() %>% 
#  rename("release_date"=".")
  
  # Extract the vote_average as a 1 column tibble
#  prep_movies3 <- qry_movies %>% 
#  map(extract, "vote_average") %>% 
#  flatten() %>% 
#  tibble() %>% 
#  rename("vote_average"=".")
  
  # Extract the overview as a 1 column tibble
#  prep_movies4 <- qry_movies %>% 
#  map(extract, "overview") %>% 
#  flatten() %>% 
#  tibble() %>% 
#  rename("overview"=".")

  # Binding all columns to create one tibble of results
#  bind_cols(
#  prep_movies1,
#  prep_movies2,
#  prep_movies3,
#  prep_movies4
#  ) %>% 
#  filter(original_title!="NA")

}

result_movies_1 <- get_movie_details(qry_Pixar_movies1)

result_movies_2 <- get_movie_details(qry_Pixar_movies2)

result_Pixar_movies <- bind_rows(result_movies_1, result_movies_2) %>% 
  rownames_to_column() %>% 
  rename("#"="rowname")

```
  
Sadly, the runtime for each movie is not available in the results. So I will 
here show the ranking (by descending revenue), the title, release date and 
the overview of the film.  
Here is the table with all the movies from **Pixar**, with a runtime **greater** 
**than one hour** and **sorted by descending revenue**:  

```{r Data_result_p3, message=FALSE, warning=FALSE}

result_Pixar_movies %>%  
  rename(
    "Title"=original_title,
    "Released"=release_date,
    "Average rating"=vote_average,
    "Overview"=overview
  ) %>%
  kable(format = "html",escape=F) %>% 
  kable_styling(
    bootstrap_options = c("striped", "condensed", "responsive", "bordered"),
    font_size = 11
  )  %>% 
  column_spec(column = 1, width = "1cm", bold = F) %>% 
  column_spec(column = 2, width = "3.5cm", bold = T) %>% 
  column_spec(column = 3, width = "2cm", bold = F) %>% 
  column_spec(column = 4, width = "2.5cm", bold = F) 

```


