---
title: "Project 4 / Report"
output:
  html_document:
    toc: true
    toc_float: true
    df_print: paged
    theme: cerulean
    highlight: zenburn
  html_notebook: default
editor_options: 
  chunk_output_type: inline
---
  
# A rental website
  
```{r Init_lib_theme, message=FALSE, warning=FALSE}

# Deactivate messages and warnings from running code, show code chunks

# Start with loading all the necessary libraries
library(dplyr)
library(tidyr)
library(rmarkdown)
library(ggplot2)
library(leaflet)
library(ggmap)
library(dplyr)
library(purrr)
library(stringr)
library(knitr)
library(kableExtra)
library(httr)
library(scales)
library(magrittr)
library(rvest)

# Load personal theme for ggplot2
myTheme <- function(base_size = 7.5,
                    base_family = "sans",
                    base_line_size = base_size / 22,
                    base_rect_size = base_size / 22){
  theme_minimal(base_size=base_size,
                base_family=base_family,
                base_line_size=base_line_size,
                base_rect_size=base_rect_size) %+replace%
  theme(
  line = element_line(
    size = base_line_size,
    linetype = 1,
    lineend = "round",
    color = "grey75"
    ),
  text = element_text(
    face = "plain",
    color = "grey25",
    family = "sans",
    size = base_size,
    hjust = 0,
    vjust = 0,
    angle = 0,
    lineheight = 1,
    margin= margin(),
    debug=FALSE
    ),
  plot.background = element_rect(
    fill = "grey98",
    color = "grey75",
    size = 1,
    linetype = 1
    ),
  panel.background = element_rect(fill="grey95",color="grey75"),
  axis.line = element_line(color="grey50", size=0.25),
  axis.ticks = element_line(color="grey50", size=0.25),
  axis.text = element_text(face="bold", size = 9),
  axis.title = element_text(face = "bold", size = 11, hjust = 0.5, vjust = 0),
  legend.text = element_text(face = "bold"),
  legend.title = element_text(face = "bold", size = 8),
  panel.grid.major.x = element_line(color="grey75"),
  panel.grid.major.y = element_line(color="grey75"),
  panel.grid.minor = element_line(color="grey90"),
  plot.margin=unit(c(12,12,12,12), "points"),
  plot.title = element_text(face = "bold", size = 12),
  plot.subtitle = element_text(
    face = "italic",
    size = 10,
    margin = margin(3,0,12,0,"pt")
    ),
  complete = TRUE
)
}

```
  
-------------------------------------------------------------------  
  
*In this fourth project, we will extract data from a website by scraping it.*

  
*The internet site is a fake rental agency, set up for this report.*  
*You can check it out [here](https://epfl-exts.github.io/rental-scrape/).*
  
  
  
  
-------------------------------------------------------------------  

## Part 1 / Scrape the website and generate a clean table of data 
  
For the first part of this report, the challenge is to scrape all the data 
from the given website and generate a tibble with it.

So here is the code followed by a table with the result :
    
```{r Data_import_prep, message=FALSE, warning=FALSE}

# Import the data from the internet site
website_html <- read_html("https://epfl-exts.github.io/rental-scrape/")

# Create lists of extracted data 
location_extract <- website_html %>% 
  html_nodes(".col-sm .sec-info .address") %>% 
  html_text() %>% 
#  str_replace_all("\\\\","") %>% 
  str_conv("UTF8") 

# Correct unformatted signs (ï)
location_ <- location_extract %>% 
  str_replace_all("Ø","") %>% 
  str_replace_all("√","ï") %>% 
  str_replace_all("\\\\","")

price_extract <- website_html %>% 
  html_nodes(".col-sm .bg-text .price .float-right strong") %>% 
  html_text() %>% 
  str_replace("Price on request",NA_character_)

currency_extract <- website_html %>% 
  html_nodes(".col-sm .bg-text .price .float-right") %>% 
  html_text() %>% 
  word(-1) %>% 
  str_replace("NA",NA_character_)

object_type_extract <- website_html %>% 
  html_nodes(".col-sm .bg-text .object-type") %>% 
  html_text()

rooms_extract <- website_html %>% 
  html_nodes(".col-sm .bg-text .rooms") %>% 
  html_text(trim = TRUE) %>% 
  str_replace_all("\\s","") %>% 
  str_extract_all("[:digit:][:digit:]|[:digit:].[:digit:]|[:digit:]") %>%
  lapply(function(x) if(identical(x, character(0))) NA_character_ else x) %>% 
  unlist()

living_space_extract <- website_html %>% 
  html_nodes(".col-sm .sec-info .living-space strong") %>% 
  html_text() %>% 
  str_replace(" m2", "") %>% 
  str_replace("NA",NA_character_)

floor_extract <- website_html %>% 
  html_nodes(".col-sm .sec-info .floor strong") %>% 
  html_text() %>% 
  str_replace("NA",NA_character_)

availability_extract <- website_html %>% 
  html_nodes(".col-sm .availability strong") %>% 
  html_text() %>% 
  str_replace("NA",NA_character_)

usable_surface_extract <- website_html %>% 
  html_nodes(".col-sm .sec-info .usable-surface strong") %>% 
  html_text()  %>% 
  str_replace(" m2", "") %>% 
  str_replace("NA",NA_character_)

# Create a tibble gathering all the lists
tbl_rental_offers <- bind_cols(
  location = location_extract,
  price = price_extract,
  currency = currency_extract,
  object_type = object_type_extract,
  rooms = rooms_extract,
  living_space = living_space_extract,
  floor = floor_extract,
  availability = availability_extract,
  usable_surface = usable_surface_extract
  ) %>% 
  mutate(
    price = as.numeric(price),
    rooms = as.numeric(rooms),
    floor = as.numeric(floor),
    living_space = as.numeric(living_space),
    usable_surface = as.numeric(usable_surface)
  ) 


# And add a table to see the result
# Generate the table of results
tbl_rental_offers %>%  
  arrange(desc(price)) %>%
  rename(
    "Address"=location,
    "Price"=price,
    "Currency"=currency,
    "Type of housing"=object_type,
    "Rooms"=rooms,
    "Living m2"=living_space,
    "Floor"=floor,
    "Availability"=availability,
    "Usable m2"=usable_surface
  ) %>%
  kable(format = "html",escape=F) %>% 
  kable_styling(
    bootstrap_options = c("striped", "condensed", "responsive", "bordered"),
    font_size = 11
  ) %>% 
  scroll_box(width = "100%", height = "480px", fixed_thead = TRUE) 
```
  
  
  
-------------------------------------------------------------------  

## Part 2 / Scatter plot showing how prices evolve with living space  
  
For the second part of this report, we will draw a scatter plot showing the 
evolution of price compared to the living space for flats.  
  
  
```{r Graph_p2, message=FALSE, warning=FALSE}

# Set a vector with all the types that match flats, for easy filtering of table
vec_flat_type <- c("Apartment","Attic flat","Duplex","Loft","Roof flat",
                   "Studio","Terrace flat")

scatterplot_price_by_space <- tbl_rental_offers %>% 
  filter(
    object_type %in% vec_flat_type,
    price < 20000, !is.na(price),
    !is.na(living_space)
  )

scatterplot_price_by_space %>% 
  ggplot(aes(x = living_space, y = price)) +
  geom_jitter(color = "steelblue3", alpha = 0.6, size = 2) +
  scale_x_continuous(labels = label_number(suffix = " m2")) +
  scale_y_continuous(labels = label_number(suffix = " CHF", big.mark = "'")) +
  labs(
    title = "Evolution of price by living space ",
    subtitle = "Comparing flats under the limit of 20'000 CHF (no houses)",
    x = "Living space",
    y = "Price"
  ) +
  myTheme() +
  theme(
    axis.text.x = element_text(hjust = 0.5),
    axis.text.y = element_text(vjust = 0.5),
    axis.title.x = element_text(margin = margin(8,0,0,0,"pt")),
    axis.title.y = element_text(margin = margin(0,8,0,0,"pt")),
    legend.position = "none"
  )

```
   
  
### Part 2 Findings  
  
In the "standard" range of living space (up to ~150 m2), the market prices 
seem to be well defined. There is a tight price range for most of the 
apartments, although some exceptions are visible.  
There are many variables to take into account such as location, standing and 
surrounding facilities in order to justify the prices' differences.  
Over ~150 m2, the prices seem to be more fluctuating. But surely some variables 
such as location, standing and number of rooms will have a bigger influence 
on the price.  
  
    
  
-------------------------------------------------------------------  

## Part 3 / Bar plot showing the number of properties by postcode  
  
For the third part of this report, we will compare the number of properties 
by postcode to see if the agency is more active in certain areas.  
  
  
```{r Graph_p3, message=FALSE, warning=FALSE}

# Get position of commas in "location" string and extract max value
comma_pos <- tbl_rental_offers$location %>%   
  str_locate_all(", ") %>%
  map(max) %>% 
  unlist() %>% 
  as_tibble()

# Extract postal code and city name from "location"
# Plus set a flag for addresses "on request"
tbl_rental_offers_with_postcode <- tbl_rental_offers %>% 
  bind_cols(comma_pos) %>% 
  filter(str_detect(location,"Ø")==FALSE) %>%
  mutate(
    city_code_name = str_sub(
      location, 
      start = value,
      end = str_length(location)
    )
  ) %>% 
  mutate(
    street = str_sub(
      location, 
      start = 0,
      end = value-2
    )
  ) %>% 
  mutate(
    postal_code = as.numeric(
      str_extract_all(
        city_code_name,
        "^.{5}"
      )
    )
  ) %>% 
  mutate(
    city = str_trim(
      str_sub(
        city_code_name,
        start = 6,
        end = str_length(city_code_name)
      )
    )
  ) %>% 
  mutate(
    onrequest_flag = if_else(
      str_detect(
        str_to_lower(location),
        "address on request"
      )|str_detect(
        str_to_lower(location),
        "sur demande"
      )|str_sub(location, start = 1, end = 1)=="-",
      TRUE,
      FALSE
    )
  )

summary_offer_by_postcode <- tbl_rental_offers_with_postcode %>% 
  group_by(postal_code,city) %>% 
  summarise(count_of_occ=n()) %>% 
  filter(count_of_occ>=10) %>% 
  ungroup()

list_postal_codes <- summary_offer_by_postcode %>% 
  select(postal_code) %>% 
  distinct() %>% 
  unlist()

# Save a table with city name and postal code
tbl_postal_codes_city <- tbl_rental_offers_with_postcode %>% 
  select(postal_code,city) %>% 
  distinct()

summary_offer_by_postcode %>%
  ggplot(
    aes(
      x = as.character(postal_code),
      y = count_of_occ,
      fill = factor(count_of_occ)
    )
  ) + 
  geom_bar(stat = "identity", position = "dodge") +
  scale_x_discrete(
    breaks = list_postal_codes,
    labels = list_postal_codes
  ) +
  scale_y_continuous(breaks = seq(0,60,10)) +
  scale_fill_grey(start = 0.5, end = 0) +
  geom_text(
    aes(y = 0, label = city),
    family = "sans",
    fontface = "bold",
    size = 4,
    color = "deepskyblue1",
    alpha = 0.75,
    angle = 90,
    hjust = 0,
    nudge_y = 1
  ) +
  labs(
    title = "A look at the number of offers by postcode",
    subtitle = str_glue("Count of offers by postcode, for the 20 most ",
                        "represented postcodes"),
    x = "Postal code",
    y = "Number of offers"
  ) +
  myTheme() +
  theme(
    axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 0.5),
    axis.text.y = element_text(vjust = 0.5),
    axis.title.x = element_text(margin = margin(8,0,0,0,"pt")),
    axis.title.y = element_text(margin = margin(0,8,0,0,"pt")),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank(),
    legend.position = "none"
  )

  
```
  
```{r Findings_p3, message=FALSE, warning=FALSE}

top_locations <- summary_offer_by_postcode %>% 
  group_by(city) %>% 
  summarise(sum_offers = sum(count_of_occ)) %>% 
  mutate(percent_of_total = sum_offers/sum(sum_offers)) %>% 
  ungroup()

winner_locations <- top_locations %>% 
  arrange(desc(sum_offers)) %>% 
  head(1)

```

    
  
### Part 3 Findings  
  
We can clearly see that this agency is very active in the city center of 
Geneva.  
  
In this top 20 locations by offers, the city center (postcodes from 1201 to 
1209) represents **`r pull(winner_locations, sum_offers)`** offers out of a 
total of **`r sum(top_locations$sum_offers)`**, which is 
**`r round(pull(winner_locations, percent_of_total)*100,2)`%** of this 
total.  
    
  
-------------------------------------------------------------------  

## Part 4 / `r str_glue("Scatter plot showing how prices evolve with living ",
                      "space, according to location and floor")`
  
For the fourth part of this report, we will draw a scatter plot showing the 
evolution of price compared to the living space for flats, and comparing it 
regarding location and floor.  
  
  
```{r Graph_p4, message=FALSE, warning=FALSE}

scatterplot_facets_price_by_space <- tbl_rental_offers_with_postcode %>% 
  filter(
    object_type %in% vec_flat_type,
    price < 20000, !is.na(price),
    !is.na(living_space),
    !is.na(floor),
    floor<=6
  ) %>% 
  mutate(floor_name=case_when(
    floor==1 ~ "1st floor",
    floor==2 ~ "2nd floor",
    floor==3 ~ "3rd floor",
    floor==4 ~ "4th floor",
    floor==5 ~ "5th floor",
    floor==6 ~ "6th floor",
    TRUE ~ "Not defined"
    )
  )

count_of_cities <- scatterplot_facets_price_by_space %>% 
  distinct(city) %>% 
  summarise(count_of_values=n()) %>% 
  unlist()

scatterplot_facets_price_by_space %>% 
  ggplot(aes(x = living_space, y = price, color = postal_code)) +
  geom_jitter(alpha = 0.8, size = 2) +
  facet_wrap(vars(floor_name)) +
  scale_color_gradientn(colors = rainbow(count_of_cities)) +
  scale_y_continuous(labels = label_number(big.mark = "'")) +
  labs(
    title = str_glue("Evolution of price regarding living space, floor ",
                    "and location"),
    subtitle = str_glue("Comparing flats under the limit of 20'000 CHF ",
                        "(no houses) \n", "Separated by floor using facets ",
                        "and postcodes using dot colors"),
    x = "Living space in m2",
    y = "Price in CHF"
  ) +
  myTheme() +
  theme(
    axis.text.x = element_text(angle = 45, vjust = 0.2, hjust = 0.2, size = 8),
    axis.text.y = element_text(vjust = 0.5, size = 8),
    axis.title.x = element_text(margin = margin(8,0,0,0,"pt")),
    axis.title.y = element_text(margin = margin(0,8,0,0,"pt")),
    legend.position = "none",
    strip.text = element_text(
      face = "bold",
      size = 9,
      hjust = 0.5,
      vjust = 0.5
    ),
    strip.background = element_rect(fill="grey85")
  )

```

```{r Findings_p4, message=FALSE, warning=FALSE}

summary_price_by_floor <- scatterplot_facets_price_by_space %>% 
  group_by(floor_name) %>% 
  summarise(mean_price=mean(price)) %>% 
  ungroup()

summary_floor_postcodes <- scatterplot_facets_price_by_space %>% 
  group_by(postal_code, floor, floor_name) %>% 
  summarise(mean_price=mean(price), count_of_offers=n()) %>% 
  arrange(desc(mean_price)) %>% 
  mutate(mean_price=as.numeric(round(mean_price, 2))) %>% 
  ungroup()

most_expensive <- summary_floor_postcodes %>% 
  head(1)  %>% 
  left_join(
    tbl_rental_offers_with_postcode,
    by = c("postal_code","mean_price"="price","floor")
  )

cheapest <- summary_floor_postcodes %>% 
  tail(1) %>% 
  left_join(
    tbl_rental_offers_with_postcode,
    by = c("postal_code","mean_price"="price","floor")
  )
  
```
  
  
### Part 4 Findings  
  
For this scatter plot, we had complete data for 
**`r nrow(scatterplot_facets_price_by_space)`** offers (including price, 
living space, location and floor).  

Same as in part 2, in the "standard" range of living space (up to ~150 m2), 
the market prices seem to be well defined. There is a tight price range for 
most of the apartments, although some exceptions are visible. The floor has 
a small influence over the price, although it seems that the prices above 
3rd floor are slightly lower.  
  
The most expensive combination "postcode/floor" is : 
**`r format(pull(most_expensive, mean_price), nsmall=2, big.mark="'")` CHF** 
on the **`r pull(most_expensive,floor_name)`**.  
This apartment is a **`r pull(most_expensive, object_type)`** of 
**`r pull(most_expensive, living_space)` m^2^** and offers 
**`r pull(most_expensive, rooms)`** rooms.  
It is located in **`r pull(most_expensive, city)`**.  
    
The cheapest combination "postcode/floor" is : 
**`r format(pull(cheapest, mean_price), nsmall=2, big.mark="'")` CHF** 
on the **`r pull(cheapest,floor_name)`**.  
This apartment is a **`r pull(cheapest, object_type)`** of 
**`r pull(cheapest, living_space)` m^2^** and offers 
**`r pull(cheapest, rooms)`** rooms.  
It is located in **`r pull(cheapest, city)`**.  

For the most expensive and cheapest "postcode/floor" combination, there was 
only one value at the extremes.  
  
  
  
-------------------------------------------------------------------  

## Part 5 / Comparing offers with "Provided address" vs "Address on request"
  
For the fifth part of this report, we will compare the offers that have an 
address with those whose address is not provided. We will try to determine 
trends, see if there are obvious reasons for not including the address in 
the offer...    
  
  
```{r Graph_p5_price, message=FALSE, warning=FALSE}

# Select records where price is available
boxplot_offers_price <- tbl_rental_offers_with_postcode %>% 
  group_by(onrequest_flag) %>% 
  filter(price>0)

summary_offers_by_price <- boxplot_offers_price %>% 
  group_by(onrequest_flag) %>% 
  summarise(
    average_price=mean(price),
    median_price=median(price)
  ) %>% 
  ungroup()

boxplot_offers_price %>% 
  ggplot(aes(x = onrequest_flag, y = price, fill = onrequest_flag)) +
  geom_boxplot(alpha = 1, size = 0.5, show.legend = FALSE) +
  geom_violin(scale = "area", alpha = 0.5, show.legend = FALSE) +
  scale_x_discrete(
    labels = c("With address","Address on request")
  ) +
  scale_y_continuous(
    labels = label_number(big.mark = "'")
  ) +
  scale_fill_manual(
    limits = c(
      "TRUE",
      "FALSE"
  ),
    values = c(
      "TRUE"="deepskyblue3",
      "FALSE"="darkslategray3"
    )
  ) +
  labs(
    title = "Comparing prices between offers with or without address",
    subtitle = str_glue("The graph represents the distribution of offers ",
                        "regarding the price by address type"),
    x = "",
    y = "Price in CHF"
  ) +
  myTheme() +
  theme(
    axis.text.x = element_text(hjust = 0.5, margin = margin(6,0,0,0,"pt")),
    axis.title.y = element_text(margin = margin(0,6,0,0,"pt")),
    legend.position = "bottom",
    legend.direction = "horizontal"
  )

```

```{r Graph_p5_living_space, message=FALSE, warning=FALSE}

# Select records where living space is available
boxplot_offers_living_space <- tbl_rental_offers_with_postcode %>% 
  filter(living_space>0)

summary_offers_by_living_space <- boxplot_offers_living_space %>% 
  group_by(onrequest_flag) %>% 
  summarise(
    average_living_space=mean(living_space),
    median_living_space=median(living_space)
  ) %>% 
  ungroup()

boxplot_offers_living_space %>% 
  ggplot(aes(x = onrequest_flag, y = living_space, fill = onrequest_flag)) +
  geom_boxplot(alpha = 1, size = 0.5, show.legend = FALSE) +
  geom_violin(scale = "area", alpha = 0.5, show.legend = FALSE) +
  scale_x_discrete(
    labels = c("With address","Address on request")
  ) +
  scale_fill_manual(
    limits = c(
      "TRUE",
      "FALSE"
  ),
    values = c(
      "TRUE"="deepskyblue3",
      "FALSE"="darkslategray3"
    )
  ) +
  labs(
    title = "Comparing living space between offers with or without address",
    subtitle = str_glue("The graph represents the distribution of offers ",
                        "regarding the living space by address type"),
    x = "",
    y = "Living surface in m2"
  ) +
  myTheme() +
  theme(
    axis.text.x = element_text(hjust = 0.5, margin = margin(6,0,0,0,"pt")),
    axis.title.y = element_text(margin = margin(0,6,0,0,"pt")),
    legend.position = "bottom",
    legend.direction = "horizontal"
  )

```
  
  
  
```{r Graph_p5_floor, message=FALSE, warning=FALSE}

# Select records where floor is available (limit max 20 floors)
boxplot_offers_floor <- tbl_rental_offers_with_postcode %>% 
  filter(floor>0&floor<20)

summary_offers_by_floor <- boxplot_offers_floor %>% 
  group_by(onrequest_flag) %>% 
  summarise(
    average_floor=mean(floor),
    median_floor=median(floor)
  ) %>% 
  ungroup()

boxplot_offers_floor %>% 
  ggplot(aes(x = onrequest_flag, y = floor, fill = onrequest_flag)) +
  geom_boxplot(alpha = 1, size = 0.5, show.legend = FALSE) +
  geom_violin(scale = "area", alpha = 0.5, show.legend = FALSE) +
  scale_x_discrete(
    labels = c("With address","Address on request")
  ) +
  scale_fill_manual(
    limits = c(
      "TRUE",
      "FALSE"
  ),
    values = c(
      "TRUE"="deepskyblue3",
      "FALSE"="darkslategray3"
    )
  ) +
  labs(
    title = "Comparing floor number between offers with or without address",
    subtitle = str_glue("The graph represents the distribution of offers ",
                        "regarding the floor number by address type"),
    x = "",
    y = "Floor #"
  ) +
  myTheme() +
  theme(
    axis.text.x = element_text(hjust = 0.5, margin = margin(6,0,0,0,"pt")),
    axis.title.y = element_text(margin = margin(0,6,0,0,"pt")),
    legend.position = "bottom",
    legend.direction = "horizontal"
  )

```
   
```{r Graph_p5_type, message=FALSE, warning=FALSE}

# Create summary table for all types of offers
plot_offers_type <- tbl_rental_offers_with_postcode %>% 
  group_by(object_type, onrequest_flag) %>% 
  summarise(count_of_offers = n())

summary_count_type <- plot_offers_type %>% 
  summarise(count_of_type = n())

plot_offers_type <- plot_offers_type %>% 
  left_join(summary_count_type, by = c("object_type")) 

plot_offers_type <- plot_offers_type %>% 
  filter(count_of_type>1)
  
plot_offers_type %>% 
  ggplot(aes(x = object_type, y = count_of_offers, fill = onrequest_flag)) +
  geom_col(position = "dodge") +
  #geom_violin(scale = "area", alpha = 0.5, show.legend = FALSE) +
  #scale_x_discrete(
  #  labels = c("With address","Address on request")
  #) +
  scale_fill_manual(
    "Address type",
    limits = c(
      "TRUE",
      "FALSE"
    ),
    values = c(
      "TRUE"="deepskyblue3",
      "FALSE"="darkslategray3"
    ),
    labels = c("Address on request","Address provided")
  ) +
  labs(
    title = "Comparing the number of offers by object type",
    subtitle = str_glue("The graph represents the distribution of offers ",
                        "regarding the type of object by address type"),
    x = "",
    y = "Count of offers"
  ) +
  myTheme() +
  theme(
    axis.text.x = element_text(
      hjust = 1, 
      vjust = 0.5, 
      margin = margin(6,0,0,0,"pt"), 
      angle = 90
    ),
    axis.title.y = element_text(margin = margin(0,6,0,0,"pt")),
    legend.position = "right",
    legend.direction = "vertical"
  )

```

  
### Part 5 Findings  
  
Comparing the data for offers with provided address or address on request shows 
some interesting facts.   
  
Here is a table comparing the average values for price, living space and floor:  
  
| **Parameter** | **Address provided** | **Address on request** |
|:--------------|:--------------------:|:----------------------:|
| **Price** |**`r round(summary_offers_by_price$average_price[1],0)`.-- CHF**|**`r round(summary_offers_by_price$average_price[2],0)`.-- CHF**|
| **Living space** |**`r round(summary_offers_by_living_space$average_living_space[1],0)` m^2^**|**`r round(summary_offers_by_living_space$average_living_space[2],0)` m^2^**|
| **Floor** |**`r round(summary_offers_by_floor$average_floor[1],2)`**|**`r round(summary_offers_by_floor$average_floor[2],2)`**|
  
  
There is a clear gap in the price and living space, where offers with an 
address on request have a much higher price for a larger living space.  
The "floor" parameter seems not determining when we consider the average and 
median values. But when looking at the box plot, we can see that there are more 
offers with address on request on lower floors.  
  
Most of the offers providing the address are apartments. On the contrary, most 
offers with an address on request are single houses.
  
We can conclude that there is a higher standing for the offers where the 
address is not provided.  
  
  
  
-------------------------------------------------------------------  

## Part 6 / Placing 30 addresses on a map
  
For the sixth and last part of this report, we will place 30 provided addresses 
on the map using the {ggmap} library and the {leaflet} library.  
  
  
```{r Graph_p6, message=FALSE, warning=FALSE}

# Select 30 addresses randomly
map_plot <- tbl_rental_offers_with_postcode %>% 
  filter(onrequest_flag==FALSE) %>% 
  group_by(postal_code) %>% 
  top_n(1, postal_code) %>% 
  head(30)

# Create list of API queries
geo_API_prefix <- "https://geocode.xyz/"
geo_API_suffix <- "?json=1"
geo_API_addresses <- map_plot %>% 
  mutate(
    location=str_replace_all(location,","," "),
    address_API=str_replace_all(location," ","+"),
  )  %>% 
  transmute(
    address_API=str_glue(
      "{geo_API_prefix}{address_API}{geo_API_suffix}"
    )
  ) %>% 
  pull()

# Query to API geo service and extract longitude and latitude
geo_coordinates <- geo_API_addresses %>% 
  map(GET) %>% 
  map(content) %>% 
  map_df(extract, c("longt","latt"))

# Final list with name, address and geo coordinates
map_plot_complete <- map_plot %>% 
  bind_cols(geo_coordinates) %>% 
  mutate(
    popup_content=str_glue(
      "{location}<br/><b>{object_type}</br>{price} {currency}</b>"
    ),
    longitude=as.numeric(longt),
    latitude=as.numeric(latt)
  ) %>% 
  select(
    location, street, postal_code, city, longitude, latitude, popup_content,
    object_type, price, currency, rooms, living_space, floor, availability
  )

map_area <- c(left=5.743817, bottom=46.051091, right=6.507367, top=46.378927)
map_base <- get_stamenmap(
  bbox = map_area,
  zoom = 10,
  maptype = "terrain"
)

ggmap(map_base) +
  geom_point(data=map_plot_complete,
             aes(x=longitude, y=latitude),alpha=0.8, color = "red", size = 4) +
  labs(title="Where are the offers of this agency located?",
       subtitle="Geo-location of 30 randomly selected offers")

```
  
  
```{r Graph_p6_bis, message=FALSE, warning=FALSE}

map_plot_complete %>% 
  leaflet() %>% 
  addTiles() %>% 
  addMarkers(
    lng = ~longitude,
    lat = ~latitude,
    popup = ~popup_content,
    label = ~location
  )

```
  
  