---
title: "Project 1 / Report"
output:
  html_document:
    toc: true
    toc_float: true
    df_print: paged
    theme: cerulean
    highlight: zenburn
  html_notebook: default
editor_options: 
  chunk_output_type: inline
---
  
# A minimal survey 
  
```{r Init_lib_theme, message=FALSE, warning=FALSE}

# Deactivate messages and warnings from running code, show code chunks

# Start with loading all the necessary libraries
library(readr)
library(janitor)
library(dplyr)
library(tidyr)
library(rmarkdown)
library(ggplot2)
library(scales)
library(dplyr)
library(purrr)
library(stringr)
library(knitr)
library(kableExtra)

# Load personal theme for ggplot2
myTheme <- function(base_size = 7.5,
                    base_family = "sans",
                    base_line_size = base_size / 22,
                    base_rect_size = base_size / 22){
  theme_minimal(base_size=base_size,
                base_family=base_family,
                base_line_size=base_line_size,
                base_rect_size=base_rect_size) %+replace%
  theme(
  line = element_line(
    size = base_line_size,
    linetype = 1,
    lineend = "round",
    color = "grey75"
    ),
  text = element_text(
    face = "plain",
    color = "grey25",
    family = "sans",
    size = base_size,
    hjust = 0,
    vjust = 0,
    angle = 0,
    lineheight = 1,
    margin= margin(),
    debug=FALSE
    ),
  plot.background = element_rect(
    fill = "grey98",
    color = "grey75",
    size = 1,
    linetype = 1
    ),
  panel.background = element_rect(fill="grey95",color="grey75"),
  axis.line = element_line(color="grey50", size=0.25),
  axis.ticks = element_line(color="grey50", size=0.25),
  axis.text.x = element_text(face="bold"),
  axis.title = element_text(face = "bold", size = 9, hjust = 0.5, vjust = 0.5),
  legend.text = element_text(face = "bold"),
  legend.title = element_text(face = "bold", size = 8),
  panel.grid.major.x = element_blank(),
  panel.grid.major.y = element_line(color="grey75"),
  panel.grid.minor = element_blank(),
  plot.margin=unit(c(12,12,12,12), "points"),
  plot.title = element_text(face = "bold", size = 12),
  plot.subtitle = element_text(
    face = "italic",
    size = 10,
    margin = margin(3,3,3,3,"pt")
    ),
  complete = TRUE
)
}

```
  
  
-------------------------------------------------------------------  
  
*Two groups (one of students and one of professors) have been asked a set of* 
*32 questions.*  
*2 CSV files are given, both containing the data from a *
*[Likert test](https://en.wikipedia.org/wiki/Likert_scale).*  
  
```{r Data_import_prep, message=FALSE, warning=FALSE}

### Chunk of code to prepare the data in tables

# Import the data (orinigal CSV files previously copied in the project folder)
tbl_students_raw <- read_csv("students.csv")
tbl_professors_raw <- read_csv("professors.csv")

# Clean the data of the 2 imports (rename unnamed columns, clean names)
# Add a column 'total_answers' to count the sum of all answers per row
# Add a column 'percent' to get the percentage of answers per question
# Add a column 'group' to identify the origin of the answers
# Order the columns
tbl_students_clean <- tbl_students_raw %>% 
  rename(question_id =X1) %>% 
  clean_names()  %>% 
  mutate(
    group="Student",
    total_answers=totally_disagree+disagree+agree+totally_agree
    ) %>% 
  mutate(
    percent=total_answers/max(total_answers)
  ) %>% 
  select(question_id,group,everything())
tbl_professors_clean <- tbl_professors_raw %>% 
  rename(question_id =X1) %>% 
  clean_names() %>%
  mutate(
    group="Professor",
    total_answers=totally_disagree+disagree+agree+totally_agree
    ) %>% 
  mutate(
    percent=total_answers/max(total_answers)
  ) %>% 
  select(question_id,group,everything())

# Regroup the data in one table to create the total values
tbl_total_answers <- bind_cols(tbl_students_clean,tbl_professors_clean)
# Calculate the total values and add label 'Total' in column 'group'
tbl_total_answers <- tbl_total_answers %>% 
  mutate(
    group="Total",
    totally_disagree=totally_disagree+totally_disagree1,
    disagree=disagree+disagree1,
    agree=agree+agree1,
    totally_agree=totally_agree+totally_agree1,
    total_answers=total_answers+total_answers1
  ) %>%  
  mutate(
    percent=total_answers/max(total_answers)
  ) %>% 
# Keep only columns related to total values (duplicates of columns end with '1')
 select(-ends_with("1"))

# Create a 'summary' table, listing all the answers by group
tbl_summary_answers <- bind_rows(
  tbl_students_clean,
  tbl_professors_clean,
  tbl_total_answers
  )

# Create a value with total number of questions
questions_count <- tbl_total_answers %>% 
  count() %>%
  as.numeric()

### With this chunk of code, I have almose all of the data ready
### Some calculations will be done bit by bit, according to the question

```
  
  
-------------------------------------------------------------------  
  
## Part 1 / Answer 3 questions  
  
In the first part of this report, I will try to answer these 3 questions :  
  
*1.*  What is the total number of answers obtained from students?  
*2.*  What is the total number of answers obtained from professors?  
*3.*  Do each question have the same number of answers?  
  
  
--------------------------------------------------------------------  
  
```{r Var_p1.1, message=FALSE, warning=FALSE}

# Chunk of code for 1st question, concerning students

# Count the number of students and the total of all answers from students
students_count <- tbl_summary_answers %>%
  filter(group=="Student") %>% 
  summarise(max(total_answers)) %>% 
  pull()

# Add up all the answers of students
students_total_answers <- tbl_summary_answers %>%
  filter(group=="Student") %>% 
  summarise(sum(total_answers)) %>% 
  pull()

# Calculate the average response rate for all questions
avg_students_total_answers <- tbl_students_clean %>% 
  summarise(avg_students_total_answers=mean(total_answers)) %>% 
  pull() %>% 
  round(2)

# Calculate the average response percentage for all questions
avg_pc_students_total_answers <- avg_students_total_answers/students_count

```
  
### *1.* What is the total number of answers obtained from students?  
  
We have a total of **`r students_count`** students that have (mostly) answered 
**`r questions_count`** questions each.  
The total number of answers obtained from students is : 
**`r students_total_answers`**  
  
The average number of answers per question is : 
**`r avg_students_total_answers`** which represents a response rate of 
**`r round(avg_pc_students_total_answers*100,2)`%**.  
  
  
  
--------------------------------------------------------------------  
  
```{r Var_p1.2, message=FALSE, warning=FALSE}

# Chunk of code for 2nd question, concerning professors

# Count the number of professors and the total of all answers from professors
professors_count <- tbl_summary_answers %>% 
  filter(group=="Professor") %>% 
  summarise(max(total_answers)) %>% 
  pull()

# Add up all the answers of professors
professors_total_answers <- tbl_summary_answers %>% 
  filter(group=="Professor") %>% 
  summarise(sum(total_answers)) %>% 
  pull()

# Calculate the average response rate for all questions
avg_professors_total_answers <- tbl_professors_clean %>% 
  summarise(avg_professors_total_answers=mean(total_answers)) %>% 
  pull() %>% 
  round(2)

# Calculate the average response percentage for all questions
avg_pc_professors_total_answers <- avg_professors_total_answers/professors_count

```
  
### *2.* What is the total number of answers obtained from professors?  
  
We have a total of **`r professors_count`** professors that have (mostly) 
answered **`r questions_count`** questions each.  
The total number of answers obtained from professors is : 
**`r professors_total_answers`**  
  
The average number of answers per question is : 
**`r avg_professors_total_answers`** which represents a response rate of 
**`r round(avg_pc_professors_total_answers*100,2)`%**.
  
  
  
--------------------------------------------------------------------  
  
```{r Var_p1.3, message=FALSE, warning=FALSE}

# Chunk of code for 3rd question, concerning the questions

# Count the number of questions with 100% answers for students
students_100pc_answers <- tbl_summary_answers %>% 
  filter(
    group=="Student",
    as.numeric(total_answers)==students_count
    ) %>% 
  summarise(n()) %>% 
  pull() %>% 
  as.numeric()

# Count the number of questions with 100% answers for professors
professors_100pc_answers <- tbl_summary_answers %>% 
  filter(
    group=="Professor",
    as.numeric(total_answers)==professors_count
    ) %>% 
  summarise(n()) %>% 
  pull() %>% 
  as.numeric()
  
# Count the number of questions with 100% answers for all
all_100pc_answers <- tbl_summary_answers %>% 
  filter(
    group=="Total",
    as.numeric(total_answers)==professors_count+students_count
    ) %>% 
  summarise(n()) %>% 
  pull() %>% 
  as.numeric()

all_not100pc_answers <- questions_count-all_100pc_answers 

# Vector with question number (question_id + 1), 100% answer rate
vec_questions_100pc_total <- tbl_summary_answers %>% 
  filter(group=="Total",percent==1) %>% 
  transmute(question_id=question_id+1) %>% 
  unlist()

# Vector with question number (question_id + 1), >95% and <100% answer rate
vec_questions_not100pc_total <- tbl_summary_answers %>% 
  filter(group=="Total",percent<1) %>% 
  transmute(question_id=question_id+1) %>% 
  unlist()

```
  
### *3.* Do each question have the same number of answers?  
  
Out of the **`r questions_count`** questions:  
  
**`r round((all_100pc_answers/questions_count*100),0)`%** or 
**`r all_100pc_answers`** questions were answered by all respondents :  
Questions : `r vec_questions_100pc_total`  
  
**`r round((all_not100pc_answers/questions_count*100),0)`%** or
**`r all_not100pc_answers`** questions were only partially answered by 
respondents  
Questions : `r vec_questions_not100pc_total`  
  
```{r Graph_p1.3, message=FALSE, warning=FALSE}

# Chunk of code to generate plot with the values for answers under
# 100% of response rate

ggplot(
  data = filter(
    tbl_summary_answers,
    group=="Professor"|group=="Student",
    question_id > 24),
  mapping = aes(x=question_id+1,y=percent),
  fill=group
  ) +
  geom_col(mapping=aes(fill=group), position="dodge", width=0.8) +
  scale_x_discrete(breaks=waiver(), limits=c(26:32))+
  scale_y_continuous(labels=scales::percent_format(accuracy = 1)) +
  scale_fill_manual(
    "Group", 
    values = c("Professor"="deepskyblue3","Student"="darkslategray3"),
    labels = c(
      str_glue("Professors (",professors_count,")"),
      str_glue("Students (",students_count,")")
      )
    ) +
  coord_cartesian(ylim=c(0.8,1)) +
  labs(title=str_glue("For the ",all_not100pc_answers,
                      " partially answered questions:"),
     subtitle = str_glue("Let's check the percentage (bar)",
      " and number of answers (label) per group"),
     x="Question number",
     y="Percentage") +
  geom_text(data = filter(tbl_summary_answers,
                          group=="Professor",
                          question_id > 24
                          ),
    mapping = aes(label = total_answers),
    family = "sans",
    fontface = "bold",
    size = 2.5,
    color = "darkslategray1",
    nudge_x = -0.2,
    nudge_y = -0.0075
    ) +
  geom_text(data = filter(tbl_summary_answers,
                          group=="Student",
                          question_id > 24
                          ),
    mapping = aes(label = total_answers),
    family = "sans",
    fontface = "bold",
    size = 2.5,
    color = "deepskyblue4",
    nudge_x = 0.2,
    nudge_y = -0.0075
    ) +
  myTheme() +
  theme(
    aspect.ratio = 2/3,
    axis.text.x = element_text(
      size = 8, 
      face = "bold.italic",
      margin = margin(3,0,0,0,unit = "pt")
    ),
    axis.title.x = element_text(margin = margin(6,0,0,0,unit = "pt")),
    axis.title.y = element_text(margin = margin(0,6,0,0,unit = "pt")),
    plot.subtitle = element_text(margin = margin(3,0,12,0,unit = "pt"))
    )

```
```{r End_p1, message=FALSE, warning=FALSE}

# Chunk of code for the findings of Part 1

pc_difference <- avg_pc_professors_total_answers-avg_pc_students_total_answers
pc_difference <- abs(round(pc_difference*100,2))

pc_diff_comment <- case_when(
  pc_difference<=1 ~"nearly a tie!",
  pc_difference<=3 ~"very close.",
  pc_difference<=5 ~"visible.",
  pc_difference<=20 ~"important...",
  TRUE ~"huge!")                     
pc_diff_comment1 <- case_when(
  pc_difference<=3 ~"this survey was well adapated to the selected groups of
  participants.",
  pc_difference<=5 ~"one group had less interest in answering these questions.",
  pc_difference<=20 ~"one group was definitely not the right choice for this
  survey",
  TRUE ~"important.")

avg_pc_total_answers <- mean(
  avg_pc_professors_total_answers,
  avg_pc_students_total_answers)
avg_pc_total_answers <- abs(round(avg_pc_total_answers*100,5))

avg_pc_comment <- case_when(
  avg_pc_total_answers>=99 ~"very satisfying, it's a success and represents 
  highly valuable data!",
  avg_pc_total_answers>=97 ~"satisfying, we can use this valuable data.",
  avg_pc_total_answers>=95 ~"ok, we can use this data.",
  avg_pc_total_answers>=80 ~"disappointing, the data is not really reliable.",
  TRUE ~"unsatisfying as the data is not reliable.")

```
  
### Part 1 Findings  
  
The difference in answer rate between professors and students is 
**`r pc_diff_comment`**  
The difference overall is of 
**`r pc_difference`%**, which indicates that **`r pc_diff_comment1`** 
  
The result of this survey is `r avg_pc_comment`  
The global response rate is **`r round(avg_pc_total_answers,2)`%**.  
  
    
  
-------------------------------------------------------------------  
  
  
## Part 2 / Side-by-side bar chart
  
For the second part of this report, here is a side-by-side bar chart
comparing the distribution of answers of the students versus the professors
for each question.  
  
```{r Graph_p2, message=FALSE, warning=FALSE}

# Chunk of code to generate side-by-side bar chart 
# Necessary libraries have been already loaded

# Prepare a summary by type of answer for the side-by-side bar chart
summary_for_facet_plot <- tbl_summary_answers %>% 
  filter(group=="Student"|group=="Professor") %>% 
  select(-total_answers,-percent) %>% 
  gather("totally_disagree","disagree","agree","totally_agree",
         key = "type_of_response", value = "count_of_response")

summary_for_facet_plot %>%
  ggplot(mapping = aes(x = type_of_response, y = count_of_response)) +
  geom_bar(mapping= aes(fill=group), stat="identity", position="dodge") +
  facet_wrap(vars(question_id+1),ncol = 6) +
  scale_x_discrete(
    breaks=waiver(),
    limits=c("totally_agree", "agree","disagree","totally_disagree"),
    labels=c("Totally Agree","Agree","Disagree","Totally Disagree")
    )+
  scale_fill_manual("Respondent",
    values = c("Professor"="deepskyblue3","Student"="darkslategray3"),
    labels = c("Professors","Students")
    ) +
  labs(title="Number of answers per question, Students versus Professors",
   subtitle = str_glue("For each question, we can see the distribution ",
    "of answers per group"),
   x="Type of answer",
   y="Number of answers") +
  myTheme() +
  theme(
    axis.text.x = element_text(
      angle = 90, hjust = 1, vjust = 0.2,
      face = "bold", size = 6,
      margin = margin(3,0,0,0,unit = "pt")
      ),
    axis.text.y = element_text(size = 6),
    legend.position = c(0.89,-0.18),
    strip.text.x = element_text(face = "bold.italic", size = 7, hjust= 0.5)
    )

```
  
  
### Part 2 Findings  
  
It seems that globally, professors and students agree to the same questions, 
with more disparity by the students. We will dive deeper into this in the 
third and last part of this report.  
  
  
-------------------------------------------------------------------  
    
  
## Part 3 / What is the general tendency for each question
  
For the third part of this report, we calculate the mode (most occuring answer) 
for each question and separated by group. This should allow us to see a central 
tendency and find if professors and students are globally answering the same.  
  
On the same side-by-side bar chart, but only showing the top answers, we can
visually see what questions oppose or gather professors and students considering
a general tendency.  
For example, the professors and the students are totally opposed on questions #
16 and #17 (tendency...). On the other hand, the first 15 questions had the
same answer as top score for both groups.  
  
```{r Graph_p3, message=FALSE, warning=FALSE}

# Chunk of code to have a complete table of values showing the mode of each
# question by group, plus the difference of answers between the groups

tbl_color_palette <- tibble(
  x=0:3,
  y=c("limegreen","palegreen","orange","orangered")
)

# Create a table with the top 1 answer by group and by question
tbl_top_answers <- summary_for_facet_plot %>% 
  group_by(question_id,group) %>% 
  arrange(desc(count_of_response)) %>% 
  top_n(1,count_of_response) %>% 
  ungroup() %>% 
  arrange(question_id) %>% 
# Add a column to give a numeric value to the type of answer
  mutate(answer_value=case_when(
    type_of_response=="totally_agree"~4,
    type_of_response=="agree"~3,
    type_of_response=="disagree"~2,
    type_of_response=="totally_disagree"~1,
  ))
# Spread the newly created table to calculate the 'weight' of each answer
# --> Numeric difference between professors' and students' types of answer
tbl_top_answers_diff <- tbl_top_answers %>%  
  select(question_id,answer_value,group) %>% 
  spread(key = group,value=answer_value) %>% 
  mutate(answer_weight=abs(Professor-Student))

# Spread again to create table with the top value
tbl_top_answers_count <- tbl_top_answers %>%  
  select(question_id,count_of_response,group) %>% 
  spread(key = group,value=count_of_response)

# Spread the newly created table to calculate the type of answer of each group
tbl_top_answers_type_of_response <- tbl_top_answers %>%  
  select(question_id,type_of_response,group) %>% 
  spread(key = group,value=type_of_response) %>%
  map(str_to_title,locale="en") %>% 
  map(str_replace,"_"," ") %>%
  as_tibble() %>% 
  mutate(question_id=as.integer(question_id)) %>% 
  left_join(tbl_top_answers_diff, by="question_id") %>% 
  left_join(tbl_top_answers_count, by="question_id") %>% 
  mutate(question_id=question_id+1)

# Regroup the top answers by group and by question with the 'weight'
tbl_top_answers <- tbl_top_answers %>%
  left_join(tbl_top_answers_diff, by="question_id") %>% 
  select(question_id,
         group,
         type_of_response,
         count_of_response,
         answer_value,
         answer_weight
         )

tbl_top_answers %>%
  ggplot(mapping = aes(x = type_of_response, y = count_of_response)) + 
### Layer geom_rect as a test, but it is visually confusing... Not implemented
#  add 'color=as.factor(answer_weight)' in ggplot(aes())
#  and unmark scale_color_manual
#  geom_rect(mapping=aes(
#    color=as.factor(answer_weight),xmin=0,xmax=5,ymin=0,ymax=150),
#    alpha=0,show.legend = FALSE,
#    linetype="solid",size=0.5) +
    geom_bar(mapping= aes(fill=group), stat="identity", position="dodge") +
  facet_wrap(vars(question_id+1),ncol = 6) +
  scale_fill_manual("Respondent",
    values = c("Professor"="deepskyblue3","Student"="darkslategray3"),
    labels = c("Professors","Students")
    ) +  
  scale_x_discrete(
    breaks=waiver(),
    limits=c("totally_agree", "agree","disagree","totally_disagree"),
    labels=c("Totally Agree","Agree","Disagree","Totally Disagree"),
    ) +
#  scale_color_manual(
#    breaks=NULL,
#    labels=NULL,
#    values=c("0"="limegreen","1"="palegreen","2"="orange","3"="orangered")
#  ) +
  labs(title="Top answer per question, Students versus Professors",
   subtitle = str_glue("For each question, which answer gathered ",
    "the most votes per group"),
   x="Type of answer",
   y="Number of answers") +
  myTheme() +
  theme(
    axis.text.x = element_text(
      angle = 90, hjust = 1, vjust = 0.2,
      face = "bold", size = 6,
      margin = margin(3,0,0,0,unit = "pt")
      ),
    axis.text.y = element_text(size = 6),
    legend.position = c(0.89,-0.18),
    strip.text.x = element_text(face = "bold.italic", size = 7, hjust= 0.5)
    )

```
  
Let's take a look at the top answer per question and per group. I also added a
color indicator ("Comp") to quickly spot the difference -if any- between our
two groups.  
  
  
```{r Tbl_p3, message=FALSE, warning=FALSE}

# Chunk of code to generate table of answers comparison by group for each
# question

tbl_top_answers_type_of_response %>% 
  # Add cell_spec to determine (visual) properties
  mutate(
    question_id=cell_spec(question_id, "html", align = "justify"),
    Professor=cell_spec(Professor, "html", align = "justify"),
    Student=cell_spec(Student, "html", align = "justify"),
    answer_weight=cell_spec(answer_weight, "html",
          align = "justify",
          background = factor(answer_weight, tbl_color_palette$x,
                        tbl_color_palette$y),
          color = factor(answer_weight, tbl_color_palette$x, 
                        tbl_color_palette$y)
          )
  ) %>% 
  select(question_id,answer_weight,Professor.x,Professor,Student.x,Student) %>% 
  rename(
    "#"=question_id,
    "Comp"=answer_weight,
    "Top Answer"=Professor.x,
    "Count"=Professor,
    "Top Answer"=Student.x,
    "Count"=Student) %>%
  kable(format = "html",escape=F) %>% 
  kable_styling(bootstrap_options = c("striped", "condensed", "responsive"),
                font_size = 11) %>% 
  column_spec(column = 1, width = "1cm", bold = T, border_left = T) %>% 
  column_spec(column = 2, width = "1cm", bold = T) %>% 
  column_spec(column = 3, width = "4cm", bold = F, border_left = T) %>% 
  column_spec(column = 4, width = "1.5cm", bold = F) %>% 
  column_spec(column = 5, width = "4cm", bold = F, border_left = T) %>% 
  column_spec(column = 6, width = "1.5cm", bold = F, border_right = T) %>% 
  add_header_above(c("Question"=2,"Professors"=2,"Students"=2))

```
  
  

```{r End_p3, message=FALSE, warning=FALSE}

# Chunk of code for the findings of part 3

tbl_count_answer_weights <- tbl_top_answers %>%
  filter(group=="Student") %>% 
  group_by(answer_weight) %>% 
  summarise(count_answer_weight=n()) %>% 
  ungroup() %>% 
  mutate(pc_of_total=round(count_answer_weight/32*100,2))

vec_pc_of_total = tbl_count_answer_weights %>% 
  pull(3)
vec_count_of_answer_weights <- tbl_count_answer_weights %>% 
  pull(2)

```
  
### Part 3 Findings  
  
Globally speaking, the professors and the students share the same view on :  
**`r vec_count_of_answer_weights[1]`** questions (**`r vec_pc_of_total[1]`%**)  
They are totally opposed on only :  
**`r vec_count_of_answer_weights[4]`** questions (**`r vec_pc_of_total[4]`%**)  
  

```{r Report1, message=FALSE, warning=FALSE}
```
